---
title: "Data Creation"
author: "Jes Stevens, M.A."
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output:
params:
  month: December                      # Refers to the month throughout the .Rmd Document | Change this to reflect the month you are analyzing
  pastyear: 2019                      # Refers to the previous year throughout the .Rmd Document | Change this when your year changes
  year: 2020                          # Refers to the current year you are analyzing | Change this when your year changes
  ytd: "2020-01-01"                   # Compiles Year to Date Dataset for this year | Leave at January 1st 2020
  date: "2020-12-01"                  # Pulls in the data for the most recent month | Change this each month
  pastdate: "2019-01-01"              # Compiles Year to Date Dataset for previous year | Leave at January 1st 2019
  pstdtmonth: "2019-12-01"            # Compiles Data for the most recent month of the previous year | This is the first day of the month
  pstdtmonth2: "2019-12-31"           # Compiles Data for the most recent month of the previous year | This is the last day of month | Must be the 30th or 31st
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction 

[Washington University Medical Center Redevelopment Corporation](http://wumcrc.com) is a partnership between BJC Health Care and Washington University School of Medicine and works to improve the quality of life for the neighborhoods surrounding the medical campus. In order to achieve this goal in Forest Park Southeast and the Central West End , WUMCRC has invested millions of dollars toward regenerating the market for private investment in businesses and real estate, enhancing human and social service opportunities, and improving the level of physical and personal security.

One way we work to improve the level of physical & personal security is the analysis and distribution of data. The original source of this crime data is <http://slmpd.org/crimereports.shtml>. This notebook uses primarily `compstatr` to access and clean the crime data. 

## R Markdown

```{r Load Dependencies, include = FALSE}
# tidyverse packages
library(ggplot2)       # plotting data
library(stringr)       # wrappers for common string operations
library(tidyr)         # tidy data
library(dplyr)         # data manipulation
library(magrittr)      # pipe operator
library(readxl)        # read & write excel files
library(lubridate)     # time data manipulation

# spatial packages
library(tmap)         # map layouts
library(tmaptools)    # tools for handeling spatial 
library(sf)           # spatial data tools
library(ceramic)      # download online imagery tiles
library(compstatr)    # tools for STL crime data
library(raster)       # geograpic data analysis & modeling
library(ggmap)        # tools for geocoding
register_google("AIzaSyDSxwc0MKtPCOcTSPVbwiQlkZqwZ78ANCQ") #load API key for geocoding

# other packages
library(here)         # file path management
library(janitor)      # tools for examining data
library(testthat)     # tools for correcting November 2020 data
library(gateway)

dst2 <- c(7:15,27:29, 39:45,81,82,87,88)      # These are the neighborhoods that make up Police District 2
dst5 <- c(38,46:58,78)                        # These are the neighborhoods that make up Police District 5

load(here("data", "nbhd_pop10.rda"))             # Loads neighborhood population data from the 2010 Census
cs_last_update(output = "string")

#create geocoder
#geocoder <- gw_build_geocoder()
```

## Create Folders for Final Output

```{r}
# This code chunk creates the appropriate folder paths that are referred to in all of the .Rmd documents. 
# This code is necessary to knit and compile the powerpoint presentations.

here()
dir.create(getwd())
dir.create(here(file.path("results", params$year)))
dir.create(here(file.path("results", params$year, params$month)))
dir.create(here(file.path("results", params$year, params$month, "ac")))
dir.create(here(file.path("results", params$year, params$month, "bot")))
dir.create(here(file.path("results", params$year, params$month, "cwe")))
dir.create(here(file.path("results", params$year, params$month, "dbp")))
dir.create(here(file.path("results", params$year, params$month, "district-2")))
dir.create(here(file.path("results", params$year, params$month, "district-5")))
dir.create(here(file.path("results", params$year, params$month, "fp")))
dir.create(here(file.path("results", params$year, params$month, "fpse")))
dir.create(here(file.path("results", params$year, params$month, "lp")))
dir.create(here(file.path("results", params$year, params$month, "sdb")))
dir.create(here(file.path("results", params$year, params$month, "vd")))
dir.create(here(file.path("results", params$year, params$month, "vp")))
dir.create(here(file.path("results", params$year, params$month, "we")))
dir.create(here(file.path("results", params$year, params$month, "mc")))
dir.create(here(file.path("results", "presentations",  params$year)))
dir.create(here(file.path("results", "presentations",  params$year, params$month)))
```


## Tidy data
### Get Crime Data

```{r Pull current and last year Data}
i <- cs_create_index()
yearlist_past <- cs_get_data(year = params$pastyear, index = i)
yearlist_pres <- cs_get_data(year = params$year, index = i)        # Constructs a table for finding a table of crime data
cs_validate(yearlist_past, year = 2019)                            # Identifies problems with SLMPD Data
cs_validate(yearlist_pres, year = 2020)
#correct November 2020 issues
# extract data and unit test column name
nov20 <- cs_extract_month(yearlist_pres, month = "November")
expect_equal("ycoord" %in% names(nov20), TRUE)

# standardize variable names
nov20 <- rename(nov20, y_coord = ycoord)

# replace data
yearlist_pres <- cs_replace_month(yearlist_pres, month = "November", monthData = nov20)

# validate
expect_equal(cs_validate(yearlist_pres, year = "2020"), TRUE)

# Identifies problems with SLMPD Data
```

#### Standardize Data for Cleaning

```{r Standardize current and past year Data}
totalCrimes_past <- cs_collapse(yearlist_past)
ytdCrimes <- cs_collapse(yearlist_pres) 
```

### Clean & Categorize Data 
#### Current Year

`cs_filter_count` removes negative counts. Negative counts, -1, in the count column means that the crime, or charge in this specific observation has either been deemed unfounded, or the crime has been up coded. We do not want to map this data. 

Many of the analyses we conduct include comparisons between violent & non-violent crime, comparisons on the amount of crimes happening in each crime cateogy over time, and if crimes occur during the day or at night. The following code ceates variables to conduct these analyses. 

`cs_crime_cat` creates a variable with the names of the crime. 

`cs_crime` creates a logic variable and codes categories of crimes as either `TRUE` or `FALSE` based on the input.

`cs_parse_date` creates two columns separating the `Date Occur` variable. The two colums are as follows: one contains the date - month, date, and year, and the other contains the hour and minute. This is used because crimes coded in the most recent month, can contain dates that occured, in previous months or years & in this report we only want to map the crimes that occured in the past month. 

`filter` is a `dplyr` function that filters out any dates that occur before the our selected date, and also filters out crimes that did not happen in either District 2 or district 5. 

`mutate` adds a variable that codes and labels the days of the week for each crime that occurred, and creates another time of day variable. 

`strptime` and `format` takes the new time variable and formats it to a character so that we can determine if the crime occured at day or at night, and creates a second coded variable that labels each observations as day or night based on the newly formated time variable. 

`select` drops the unneeded variables. 

`cs_missing_XY` determines what data does not have x & y coordinates, and therefore cannot be accurately mapped. 

`cs_replace0` replaces missing x & y coordinates with `NA`, and drops the missing data. 

`strptime` and `format` takes the new time variable and formats it to a character so that we can determine if the crime occured at day or at night, and creates a second coded variable that labels each observations as day or night based on the newly formated time variable. 

`select` drops the unneeded variables. 

`monthCrimes` is an object that holds crimes for the current month of this year. 

```{r Creates current year Tidy Crime File}
ytdCrimes <- ytdCrimes %>% 
  cs_filter_count(., var = count) %>%                                                     # Removes Negative Counts
  cs_filter_crime(., var = crime, "part 1") %>%                                           # Filters Part 1 Crimes
  cs_crime_cat(., var = crime, crimeCatNum, "numeric") %>%                                # Creates numeric categorical variable of crimes
  cs_crime_cat(., var = crime, crimeCatName, "string") %>%                                # Creates categorical variable of crimes | String
  cs_crime(., var = crime, violent, "violent") %>%                                        # T/F Categorical Variable of Violent Crime
  cs_crime(., var = crime, property, "property") %>%                                      # T/F Categorical Variable of Property Crime
  cs_parse_date(., date_occur, dateVar = dateOcc, timeVar = timeOcc) %>%                  # Creates new time coded variables 
  filter(district == 2 | district == 5) %>%                                               # Filters all district 2 & district 5 crime
  mutate(weekday = wday(dateOcc, label = TRUE)) %>%                                       # Creates a variable of the weekday based on previously created date variable
  mutate(monthVar = dateOcc) %>%
  # Recode values to neighborood names
  mutate(nbhd_name = ifelse(grepl("28", neighborhood), "Botanical Heights",
                            ifelse(grepl("38", neighborhood), "Central West End",
                                             ifelse(grepl("39", neighborhood), "Forest Park Southeast",
                                             ifelse(grepl("46", neighborhood), "Skinker DeBaliviere",  
                                             ifelse(grepl("47", neighborhood), "DeBaliviere Place",
                                             ifelse(grepl("48", neighborhood), "West End",
                                             ifelse(grepl("49", neighborhood), "Visitation Park",       
                                             ifelse(grepl("51", neighborhood), "Academy",       
                                             ifelse(grepl("53", neighborhood), "Fountain Park",       
                                             ifelse(grepl("54", neighborhood), "Lewis Place",       
                                             ifelse(grepl("58", neighborhood), "Vandeventer", NA))))))))))))%>%
  mutate(tod = timeOcc)%>%
  mutate(abbr = ifelse(grepl("28", neighborhood), "bot",
                       ifelse(grepl("38", neighborhood), "cwe",
                                             ifelse(grepl("39", neighborhood), "fpse",
                                             ifelse(grepl("46", neighborhood), "sdb",  
                                             ifelse(grepl("47", neighborhood), "dbp",
                                             ifelse(grepl("48", neighborhood), "we",
                                             ifelse(grepl("49", neighborhood), "vp",       
                                             ifelse(grepl("51", neighborhood), "ac",       
                                             ifelse(grepl("53", neighborhood), "fp",       
                                             ifelse(grepl("54", neighborhood), "lp",       
                                             ifelse(grepl("58", neighborhood), "vd", NA))))))))))))%>%
  drop_na("ileads_street")

ytdCrimes$monthVar <- month(as.Date(ytdCrimes$monthVar, 
                                      format="%d/%m/%Y"), label = TRUE)                   # Pulls out the Month based on the Date | i.e 10/01/2018 = "October" 

#Replace NAs with 0 to prep for geocoding
ytdCrimes$ileads_address[is.na(ytdCrimes$ileads_address)] <- 0

ytdCrimes$neighborhood <- as.numeric(ytdCrimes$neighborhood)                          # Formats the neighborhood variable as numeric
ytdCrimes$tod <- strptime(ytdCrimes$tod, tz = "America/Chicago", "%H:%M")             # Strips & Reformats the structure of the time variable
ytdCrimes$tod <- format(ytdCrimes$tod, format = "%H%M%S")

ytdCrimes <- ytdCrimes %>%
  filter(dateOcc >= as.Date(params$ytd)) %>%                                             # Filters data based on the date provided in the paramaters
  mutate(., dayNight = ifelse(tod >= "180000" & tod < "600000", 
                              "Night", "Day")) %>% 
  dplyr::select(-dateTime, -tod, -flag_crime, 
                -flag_administrative, -flag_unfounded, 
                 -flag_cleanup) 
#create district_crimes for creating district crimes maps
district_crimes <- ytdCrimes

# Filter out 10 neighborhoods we want to study
  ytdCrimes%>%
    filter(neighborhood %in% c("28", "38", "39", "46", "47", "48", "49", "51", "53", "54", "58"))->ytdCrimes
#Prepare data for geocoding
ytdCrimes <- mutate(ytdCrimes, "address" = ifelse(ytdCrimes$ileads_address > 0, paste(ytdCrimes$ileads_address, ytdCrimes$ileads_street, ", St. Louis, MO"), paste(ytdCrimes$ileads_street, ", St. Louis, MO"))) 
#Geocode
ytdCrimes <- mutate_geocode(ytdCrimes, address)

monthCrimes_pres <- ytdCrimes %>% 
    filter(dateOcc >= as.Date(params$date))                                             # Filters dataset of crimes that happened in the month determined by the parameters
```

##### Larcenies 

```{r}
# The following code filters out a dataset for an analysis of larcenies. 
# It then adds a categorical variable based the type of larceny found in the description variable. 
# It also adds another variable that categorizes the value of the larceny. 

larceny <- monthCrimes_pres %>% 
  filter(., crimeCatNum == 6)

larceny <- mutate(larceny, "type" = ifelse(grepl("ALL OTHER", description), "All Other", 
                                    ifelse(grepl("BICYCLE", description), "Bicycle", 
                                    ifelse(grepl("FROM BUILDING", description), "From Building", 
                                    ifelse(grepl("FROM COIN", description), "From Coin Machine", 
                                    ifelse(grepl("FROM MTR VEH", description), "From Motor Vehicle", 
                                    ifelse(grepl("MTR VEH PARTS", description), "Motor Vehicle Parts",
                                    ifelse(grepl("PURSE", description), "Purse Snatching",
                                    ifelse(grepl("SHOPLIFT", description), "Shoplifting",
                                    ifelse(grepl("FRM PRSN", description), "From Person",
                                    ifelse(grepl("PICKPOCKET", description), "Pickpocket", NA)))))))))))

larceny <- mutate(larceny, "value" = ifelse(grepl("UNDER", description), "Under $500",
                                     ifelse(grepl("\\$500 - \\$24,999", description), "$500 - $24,999",
                                     ifelse(grepl("OVER \\$25,000", description), "Over $25,000", NA)))) 
```

#### Past Year

```{r Total Crimes for past year Tidied}
# The following code tidies a dataset for an comparative analysis for crimes that occurred last year
# It is formated to match the current year's dataset. 

totalCrimes_past <- totalCrimes_past %>% 
  cs_filter_count(., var = count) %>%
  cs_filter_crime(., var = crime, "part 1") %>%
  cs_crime_cat(., var = crime, crimeCatNum, "numeric") %>%
  cs_crime_cat(., var = crime, crimeCatName, "string") %>%
  cs_crime(., var = crime, violent, "violent") %>%
  cs_crime(., var = crime, property, "property") %>%
  cs_parse_date(., date_occur, dateVar = dateOcc, timeVar = timeOcc) %>%
  filter(district == 2 | district == 5) %>%
  mutate(weekday = wday(dateOcc, label = TRUE)) %>%
  mutate(monthVar = dateOcc) %>%
  mutate(abbr = ifelse(grepl("28", neighborhood), "bot",
                                             ifelse(grepl("38", neighborhood), "cwe",
                                             ifelse(grepl("39", neighborhood), "fpse",
                                             ifelse(grepl("46", neighborhood), "sdb",  
                                             ifelse(grepl("47", neighborhood), "dbp",
                                             ifelse(grepl("48", neighborhood), "we",
                                             ifelse(grepl("49", neighborhood), "vp",       
                                             ifelse(grepl("51", neighborhood), "ac",       
                                             ifelse(grepl("53", neighborhood), "fp",       
                                             ifelse(grepl("54", neighborhood), "lp",       
                                             ifelse(grepl("58", neighborhood), "vd", NA))))))))))))%>%
  mutate(tod = timeOcc)

totalCrimes_past$monthVar <- month(as.Date(totalCrimes_past$monthVar, format="%d/%m/%Y"), label = TRUE)

totalCrimes_past$neighborhood <- as.numeric(totalCrimes_past$neighborhood)

totalCrimes_past$tod <- strptime(totalCrimes_past$tod, tz = "America/Chicago", "%H:%M")
totalCrimes_past$tod <- format(totalCrimes_past$tod, format = "%H%M%S")

totalCrimes_past <- totalCrimes_past %>%
  mutate(., dayNight = ifelse(tod >= "180000" & tod < "600000", "Night", "Day")) %>% 
  dplyr::select(-dateTime, -tod, -flag_crime, -flag_administrative, -flag_unfounded, -flag_cleanup) %>%
  cs_missingXY(., varX = x_coord, varY = y_coord, newVar = missing) %>%
  cs_replace0(., var = x_coord) %>%
  cs_replace0(., var = y_coord) %>% 
  filter(., missing == FALSE) %>% 
  filter(dateOcc >= as.Date(params$pastdate))

monthCrimes_past <- totalCrimes_past %>% 
    filter(dateOcc >= as.Date(params$pstdtmonth) & dateOcc <= as.Date(params$pstdtmonth2))

ytdCrimes_past <- totalCrimes_past%>% 
    filter(dateOcc <= as.Date(params$pstdtmonth2))
```


### Get Spatial Data 

#### External Shapefiles 

```{r Load Shapefiles, include=FALSE}
st_read(here("data", "external", "med-campus", "medcampus.shp"))%>%
  st_transform(crs = 4296)-> med_campus

st_read(here("data", "external", "cortex-boundary", "CORTEX BOUNDARY.shp")) %>%
  st_transform(crs = 4296) -> cortex

st_read(here("data", "external", "grove-cid", "grovecid.shp")) %>%
  st_transform(crs = 4296) -> grove_cid

st_read(here("data", "external", "stl_neighborhoods", "nbhds.shp")) %>%
  st_transform(crs = 4296) %>% 
  rename(., "neighborhood" = NHD_NUM)-> nhoods_sf

save(med_campus, cortex, grove_cid, nhoods_sf, file = here("data", "basemap-files", "boundaries.rda"))
```

```{r Create SF objects for past year & current year Crimes}
# all crimes 
monthCrimes_pres_sf <- st_as_sf(x = monthCrimes_pres,                         
           coords = c("lon", "lat"),
           crs = 4296)
ytdCrimes_sf <- st_as_sf(x = ytdCrimes,                         
           coords = c("lon", "lat"),
           crs = 4296)
totalCrimes_past_sf <- cs_projectXY(totalCrimes_past, varX = x_coord, varY = y_coord, crs = 4296)
ytdCrimes_past_sf <- cs_projectXY(ytdCrimes_past, varX = x_coord, varY = y_coord, crs = 4296)
monthCrimes_past_sf <- cs_projectXY(monthCrimes_past, varX = x_coord, varY = y_coord, crs = 4296)

larceny_sf <- cs_projectXY(larceny, varX = x_coord, varY = y_coord, crs = 4296)

# med campus
mc_crimes_past_sf <- st_intersection(monthCrimes_past_sf, med_campus) 
mc_crimes_past <- mc_crimes_past_sf  %>% 
   as.data.frame()

mc_crimes_pres_sf <- st_intersection(monthCrimes_pres_sf, med_campus)
mc_crimes_pres <- mc_crimes_pres_sf  %>% 
   as.data.frame()

mc_crimes_ytdpast_sf <- st_intersection(ytdCrimes_past_sf, med_campus) 
mc_crimes_ytdpast <- mc_crimes_ytdpast_sf %>% 
   as.data.frame() 

mc_crimes_ytdpres_sf <- st_intersection(ytdCrimes_sf, med_campus)
mc_crimes_ytdpres <- mc_crimes_ytdpres_sf %>% 
   as.data.frame()

mc_crimes_totpast_sf <- st_intersection(totalCrimes_past_sf, med_campus)
mc_crimes_totpast <- mc_crimes_totpast_sf %>% 
   as.data.frame()

mc_larcenies_sf <- st_intersection(larceny_sf, med_campus)
mc_larcenies <- mc_larcenies_sf %>% 
   as.data.frame()

# cortex
ctx_crimes_sf <- st_intersection(monthCrimes_pres_sf, cortex)

# police districts 
dst_2 <- district_crimes %>% 
  filter(., neighborhood %in% dst2) %>% 
  group_by(., neighborhood) %>%
  count() %>% 
  rename(crimeTotal = n) %>%
  left_join(nbhd_pop10, by = "neighborhood") %>% 
  mutate(., crimeRate = (crimeTotal/pop10)*1000) %>% 
  drop_na()

dst_5 <- district_crimes %>% 
  filter(., neighborhood %in% dst5) %>% 
  group_by(., neighborhood) %>%
  count() %>% 
  rename(crimeTotal = n) %>%
  left_join(nbhd_pop10, by = "neighborhood") %>% 
  mutate(., crimeRate = (crimeTotal/pop10)*1000) %>% 
  drop_na()

dst_2_pop_sf <- left_join(nhoods_sf, dst_2, by = "neighborhood") %>% 
  st_transform(crs = 4296) %>%
  drop_na() %>% 
  subset(., neighborhood != 88)

dst_5_pop_sf <- left_join(nhoods_sf, dst_5, by = "neighborhood") %>% 
  st_transform(crs = 4296) %>%
  drop_na()

# Save
save(totalCrimes_past_sf, ytdCrimes_past_sf, ytdCrimes_sf, monthCrimes_past_sf, monthCrimes_pres_sf, mc_crimes_past_sf, mc_crimes_pres_sf, mc_crimes_ytdpast_sf, mc_crimes_totpast_sf, mc_crimes_ytdpres_sf, mc_larcenies_sf, ctx_crimes_sf, dst_2_pop_sf, dst_5_pop_sf, file = here("data", "spatial-crime-data.rda"))

save(ytdCrimes_past, ytdCrimes, monthCrimes_past, monthCrimes_pres, totalCrimes_past, larceny, mc_crimes_past, mc_crimes_pres, mc_crimes_ytdpast, mc_crimes_totpast, mc_crimes_ytdpres, mc_larcenies, dst_2, dst_5, file = here("data", "crime-data.rda"))

```

```{r Service Area Neighborhood Coordinates and Basemap Tiles, eval= FALSE}
#### Tiles from Mapbox 

xyfpse <- c(-90.2679, -90.2423, 38.6176, 38.6334)
xycwe <- c(-90.2759, -90.2368, 38.6286, 38.6552)
xybot <- c(-90.2619, -90.2409, 38.6165, 38.6296)
xydbp <- c(-90.2869, -90.2726, 38.6433, 38.6566)
xysdb <- c(-90.3026, -90.2827, 38.6456, 38.6571)
xywe <- c(-90.3020, -90.2712, 38.6517, 38.6710)
xyvp <- c(-90.2803, -90.2712, 38.6517, 38.6622)
xyac <- c(-90.2744, -90.2609, 38.6505, 38.6661)
xyfp <- c(-90.2648, -90.2543, 38.6493, 38.6655)
xylp <- c(-90.2588, -90.2437, 38.6481, 38.6624)
xyvd <- c(-90.2520, -90.2304, 38.6426, 38.6585)
xymc <- c(-90.2678, -90.2515, 38.6305, 38.6411)
xyctx <- c(-90.2581, -90.2419, 38.6299, 38.6386)
xygrv <- c(-90.2662, -90.2440, 38.6238, 38.6318)
xydst2 <- c(-90.3203, -90.2297, 38.5613, 38.6493)
xydst5 <- c(-90.3080, -90.2132, 38.6273, 38.6962)
xysa <- c(-90.30151,-90.22332, 38.61385, 38.66346)

fpse_tiles <- raster::extent(xyfpse) %>%
  cc_location(., type = "mapbox.streets", max_tiles = 15)
cwe_tiles <- raster::extent(xycwe) %>% 
  cc_location(., type = "mapbox.streets", max_tiles = 15)
bot_tiles <- raster::extent(xybot) %>%
  cc_location(., type = "mapbox.streets", max_tiles = 15)
dbp_tiles <- raster::extent(xydbp) %>% 
  cc_location(., type = "mapbox.streets", max_tiles = 15)
sdb_tiles <- raster::extent(xysdb) %>%
  cc_location(., type = "mapbox.streets", max_tiles = 15)
we_tiles <- raster::extent(xywe) %>% 
  cc_location(., type = "mapbox.streets", max_tiles = 15)
vp_tiles <- raster::extent(xyvp) %>%
  cc_location(., type = "mapbox.streets", max_tiles = 15)
ac_tiles <- raster::extent(xyac) %>% 
  cc_location(., type = "mapbox.streets", max_tiles = 15)
fp_tiles <- raster::extent(xyfp) %>% 
  cc_location(., type = "mapbox.streets", max_tiles = 15)
lp_tiles <- raster::extent(xylp) %>%
  cc_location(., type = "mapbox.streets", max_tiles = 15)
vd_tiles <- raster::extent(xyvd) %>% 
  cc_location(., type = "mapbox.streets", max_tiles = 15)
mc_tiles <- raster::extent(xymc) %>% 
  cc_location(., type = "mapbox.streets", max_tiles = 15)
ctx_tiles <- raster::extent(xyctx) %>% 
  cc_location(., type = "mapbox.streets", max_tiles = 15)
grv_tiles <- raster::extent(xygrv) %>% 
  cc_location(., type = "mapbox.streets", max_tiles = 15)
dst2_tiles <- raster::extent(xydst2) %>% 
  cc_location(., type = "mapbox.streets", max_tiles = 15)
dst5_tiles <- raster::extent(xydst5) %>% 
  cc_location(., type = "mapbox.streets", max_tiles = 15)

sa_tiles <- raster::extent(xysa) %>% 
  cc_location(., type = "mapbox.mapbox-streets-v7", max_tiles = 15)

save(sa_tiles, file = here("data", "basemap-files", "service-area-tiles.rda"))

load(file = here("data", "basemap-files", "mapbox-tiles.rda"))
load(file = here("data", "basemap-files", "service-area-tiles.rda"))


save(ac_tiles, bot_tiles, ctx_tiles, cwe_tiles, dbp_tiles, dst2_tiles, dst5_tiles, fp_tiles, fpse_tiles, grv_tiles, lp_tiles, mc_tiles, sa_tiles, sdb_tiles, vd_tiles, vp_tiles, we_tiles, file = here("data", "basemap-files", "mapbox-tiles.rda"))

rm(xyfpse, xycwe, xybot, xydbp, xysdb, xywe, xyvp, xyac, xyfp, xylp, xyvd, xymc, xyctx, xygrv, xydst2, xydst5)
```
```


```{r}
# This code cleans our Global Environment.

rm(list = ls())
```


