---
title: "Forest Park Southeast, Botanical Heights, Central West End, Medical Campus"
subtitle: "Monthly Crime report: April 2020" 
author: "Washington University Medical Center"
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output:
  powerpoint_presentation
always_allow_html: yes
params:
  month: May
  pastyear: 2019
  year: 2020
  date: "2020-05-01"
  pastdate: "2019-05-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Dependencies and Data, include = FALSE}
# tidyverse packages
library(ggplot2)       # plotting data
library(stringr)       # wrappers for common string operations
library(tidyr)         # tidy data
library(dplyr)         # data manipulation
library(magrittr)      # pipe operator
library(readxl)        # read & write excel files
library(lubridate)     # time data manipulation
library(scales)

# spatial packages
library(tmap)         # map layouts
library(tmaptools)    # tools for handeling spatial
#library(oldtmaptools) # deprecated toolds for spatial analysis
library(sf)           # spatial data tools
library(ceramic)      # download online imagery tiles
library(compstatr)    # tools for STL crime data
library(raster)       # geograpic data analysis & modeling

# other packages
library(here)         # file path management
library(janitor)      # tools for examining data
library(RColorBrewer) # cynthia brewer color palettes
library(viridis)      # color palettes
library(flextable)   # exporting pretty tables
library(htmltools)
library(knitr)
library(tibble)
library(rlang)
library(officer)      # powerpoint output
#devtools::install_github("davidgohel/officer")   # use github version until updates are made to CRAN
library(customLayout) # custom powerpoint layout


# load data
load(file = here("data", "basemap-files", "mapbox-tiles.rda"))
load(file = here("data", "basemap-files", "boundaries.rda"))
load(file = here("data", "crime-data.rda"))
load(file = here("data", "spatial-crime-data.rda"))
load(file = here("data", "nbhd_pop10.rda"))
load(file = here("data", "basemap-files", "nbhd-boundaries.rda"))

# create powerpoint
report <- read_pptx()
```

```{r officer layout}
lay <- lay_new(matrix(1:4, nc = 2), widths = c(2,2), heights = c(2,1)) 
title <- lay_new(1, widths = 2, heights = 2)
layout <- lay_bind_row(title, lay, heights = c(1,6))
lay_show(layout)

lay01 <- lay_new(matrix(1:2)) 
title01 <- lay_new(1, widths = 2, heights = 2)
layout01 <- lay_bind_row(title01, lay01, heights = c(1,6))
lay_show(layout01)

## create officer layouts
offlayout <- phl_layout(layout,
    margins = c(0, 1, 1, 0),
    innerMargins = rep(0.15,4))

offlayout01 <- phl_layout(layout01,
    margins = c(0.25, 0.25, 0.25, 0.25),
    innerMargins = rep(0.15,4))
```

```{r Set column name keys for flextable, include = FALSE }
colkeys19 <- totalCrimes19$monthVar
colkeys20 <- ytdCrimes20$monthVar
colkeysdys <- totalCrimes19$weekday
colkeystotal <- c("Total")
part1crimes <- c("Aggravated Assault", "Arson", "Burgalry", "Homicide", "Larceny", "Motor Vehicle Theft", "Robbery")
wkdys <- c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun")
#tmap_options()
```

```{r plot and text color palette, inlude = FALSE}
cols <- c("Aggravated Assault" = "#e41a1c", "Arson" = "#A65628", "Burgalry" = "#377eb8", 
          "Homicide" = "#FFFF33", "Larceny" = "#4DAF4A", "Motor Vehicle Theft" = "#984EA3", 
          "Robbery" = "#FF7F00") 

# summary note colors
reg24 <- fp_text(color = 'black', font.size = 24)
reg20 <- fp_text(color = 'black', font.size = 20)
boldline <- fp_text(color = "black", font.size = 28, bold = TRUE, underlined = TRUE)
bold <- fp_text(color = "black", font.size = 24, bold = TRUE)
```

```{r powerpoint title}
#title slide
report%>%
  add_slide(layout = "Title Slide", master = "Office Theme")%>%
  ph_with(value = "Forest Park Southeast, Botanical Heights, Central West End, Medical Campus", location = ph_location_type(type = "ctrTitle"))%>%
  ph_with(c(paste("Monthly Crime Report:", params$month, params$year, sep = " "), "Washington University Medical Center"), location = ph_location_type(type = "subTitle")) -> report
```

## Forest Park Southeast: Summary Notes

```{r FPSE Summary Prep, include=FALSE}
tc19 <- nrow(monthCrimes19[monthCrimes19$neighborhood == 39,])
tc20 <- nrow(monthCrimes20[monthCrimes20$neighborhood == 39,])
cap19 <- nrow(monthCrimes19[monthCrimes19$neighborhood == 39 & monthCrimes19$crimeCatNum == 4 | monthCrimes19$neighborhood == 39 & monthCrimes19$crimeCatNum == 3,])
cap20 <- nrow(monthCrimes20[monthCrimes20$neighborhood == 39 & monthCrimes20$crimeCatNum == 4 | monthCrimes20$neighborhood == 39 & monthCrimes20$crimeCatNum == 3,])

tc_ytd19 <- nrow(ytdCrimes19[ytdCrimes19$neighborhood == 39,])
tc_ytdCurrent <- nrow(ytdCrimes20[ytdCrimes20$neighborhood == 39,])
cap19_ytd <- nrow(ytdCrimes19[ytdCrimes19$neighborhood == 39 & ytdCrimes19$crimeCatNum == 4 | ytdCrimes19$neighborhood == 39 & ytdCrimes19$crimeCatNum == 3,])
cap20_ytd <- nrow(ytdCrimes20[ytdCrimes20$neighborhood == 39 & ytdCrimes20$crimeCatNum == 4 | ytdCrimes20$neighborhood == 39 & ytdCrimes20$crimeCatNum == 3,])

pct_chg_mth1 <- (tc20 - tc19)/tc19
pct_chg_mth <- percent(pct_chg_mth1)
if(is.nan(pct_chg_mth1)){pct_chg_mth[is.nan(pct_chg_mth1)] <- 0}
if(is.infinite(pct_chg_mth1)){pct_chg_mth[is.infinite(pct_chg_mth1)] <- "Infinite"}

pct_chg_cap1 <- (cap20 - cap19)/cap19
pct_chg_cap <- percent(pct_chg_cap1)
if(is.nan(pct_chg_cap1)){pct_chg_cap[is.nan(pct_chg_cap1)] <- 0}
if(is.infinite(pct_chg_cap1)){pct_chg_cap[is.infinite(pct_chg_cap1)] <- "Infinite"}

pct_chg_ytd1 <- (tc_ytdCurrent - tc_ytd19)/tc_ytd19
pct_chg_ytd <- percent(pct_chg_ytd1)
if(is.nan(pct_chg_ytd1)){pct_chg_ytd[is.nan(pct_chg_ytd1)] <- 0}
if(is.infinite(pct_chg_ytd1)){pct_chg_ytd[is.infinite(pct_chg_ytd1)] <- "Infinite"}

pct_chg_ytd_cap1 <- (cap20_ytd - cap19_ytd)/cap19_ytd
pct_chg_ytd_cap <- percent(pct_chg_ytd_cap1)
if(is.nan(pct_chg_ytd_cap1)){pct_chg_ytd_cap[is.nan(pct_chg_ytd_cap1)] <- 0}
if(is.infinite(pct_chg_ytd_cap1)){pct_chg_ytd_cap[is.infinite(pct_chg_ytd_cap1)] <- "Infinite"}

sprint_1 <- sprintf("%s total crimes in %s %s", 
                    tc20, params$month, params$year)
sprint_2 <- sprintf("%s total crimes in %s", 
                    tc_ytdCurrent, params$year)

# text formatting
color24a <- fp_text(color = ifelse(pct_chg_mth1 == 0, "#00B0F0", ifelse(pct_chg_mth < 0, "#00B050", "red")), font.size = 24)
color20a <- fp_text(color = ifelse(pct_chg_cap1 == 0, "#00B0F0", ifelse(pct_chg_cap < 0, "#00B050", "red")), font.size = 20)
color24b <- fp_text(color = ifelse(pct_chg_ytd1 == 0, '#00B0F0', ifelse(pct_chg_ytd < 0, '#00B050', 'red')), font.size = 24)
color20b <- fp_text(color = ifelse(pct_chg_ytd_cap1 == 0, "#00B0F0", ifelse(pct_chg_ytd_cap < 0, "#00B050", "red")), font.size = 20)

# create summary notes
summary <- block_list(
  fpar(ftext(sprint_1, boldline)),
  fpar(ftext(paste(pct_chg_mth, "change ", sep = " "), color24a),
       ftext(paste("compared to ", params$month, " ", params$pastyear, " (", tc19, " total crimes)", sep = ""), reg24)),
  fpar(ftext(paste(cap20, "crime(s) against persons", sep = " "), bold),
       ftext(paste(" in", params$month, params$year, sep = " "), reg24)),
  fpar(ftext(paste(pct_chg_cap, "change", sep = " "), color20a),
       ftext(paste(" compared to ", params$month, " ", params$pastyear, " (", cap19, " crimes against persons)", sep = ""), reg20)),
  fpar(ftext(sprint_2, boldline)),
  fpar(ftext(paste(pct_chg_ytd, "change ", sep = " "), color24b),
       ftext(paste("compared to this time in ", params$pastyear, " (", tc_ytd19, " total crimes)", sep = ""), reg24)),
  fpar(ftext(paste(cap20_ytd, "crime(s) against persons", sep = " "), bold),
       ftext(paste(" in", params$year, sep = " "), reg24)),
  fpar(ftext(paste(pct_chg_ytd_cap, "change", sep = " "), color20b),
       ftext(paste(" compared to this time in ", params$pastyear, " (", cap19_ytd, " crimes against persons)", sep = ""), reg20))
)

# write summary notes to powerpoint slide
report%>%
  add_slide(layout = 'Title and Content', master = 'Office Theme')%>%
  ph_with(value = "Forest Park Southeast: Summary Notes", location = ph_location_type(type = "title"))%>%
  ph_with(summary, location = ph_location_type(type = "body"), is_list = TRUE, level_list = c(1, 2, 2, 3, 1, 2, 2, 3)) -> report
```

## Forest Park Southeast: Year to Year Comparison

```{r FPSE Year Comps Prep, include=FALSE}
totalCrimes19 %>%
  filter(., neighborhood == 39) %>%
  group_by(monthVar, .drop = FALSE) %>%
  count(crimeCatName) %>%
  rename(., "Number of Crimes" = n) %>%
  pivot_wider(names_from = monthVar, values_from = "Number of Crimes") %>%
  replace(., is.na(.), 0)  -> fpse_2019

ytdCrimes20 %>%
  filter(., neighborhood == 39) %>%
  group_by(monthVar) %>%
  count(crimeCatName) %>%
  rename(., "Number of Crimes" = n) %>%
  pivot_wider(names_from = monthVar, values_from = "Number of Crimes") %>%
  replace(., is.na(.), 0) -> fpse_2020
```

```{r FPSE Total Crimes Flextable 2019, echo = FALSE}
part1crimes[!(part1crimes %in% fpse_2019$crimeCatName)] -> missing_category
is_empty(missing_category) -> test

if(test == FALSE) {
   add_row(fpse_2019, crimeCatName = missing_category) -> fpse_2019
}

fpse_2019 %>% 
  arrange(., crimeCatName) %>%
  replace(., is.na(.), 0) %>%
  adorn_totals(., "col", name = "Total") %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Part 1 Crimes" = crimeCatName) -> fpse_2019

flextable(fpse_2019) %>%
  colformat_num(.,  digits = 0) %>%
  colformat_num(., digits = 0) %>%
  add_header_lines(values = params$pastyear)%>%
  autofit() -> flex
```

```{r FPSE Total Crimes Flextable 2020, echo = FALSE}
part1crimes[!(part1crimes %in% fpse_2020$crimeCatName)] -> missing_category
is_empty(missing_category) -> test

if(test == FALSE) {
   add_row(fpse_2020, crimeCatName = missing_category) -> fpse_2020
}

fpse_2020 %>% 
  arrange(., crimeCatName) %>%
  replace(., is.na(.), 0) %>%
  adorn_totals(., "col", name = "Total") %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Part 1 Crimes" = crimeCatName) -> fpse_2020

flextable(fpse_2020) %>%
  colformat_num(.,  digits = 0) %>%
  colformat_num(.,  digits = 0) %>%
  add_header_lines(values = params$year)%>%
  autofit() -> flex01

# add powerpoint slide
report%>%
  add_slide()%>%
  phl_with_text(olay = offlayout01, 1, "Forest Park Southeast: Year to Year Comparison")%>%
  phl_with_flextable(olay = offlayout01, 2, flex)%>%
  phl_with_flextable(olay = offlayout01, 3, flex01) -> report
```

## Forest Park Southeast: Summary Tables

```{r FPSE Tables Prep, include = FALSE}
monthCrimes20 %>%
  filter(., neighborhood == 39) %>%
  group_by(crimeCatName, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Part 1 Crimes" = crimeCatName) -> fpse_crimeCat

monthCrimes20 %>%
  filter(., neighborhood == 39) %>%
  group_by(weekday, .drop = FALSE) %>%
  count() %>%
  rename(., "Number of Crimes" = n) %>%
  replace(., is.na(.), 0) -> fpse_weekDay

wkdys[!(wkdys %in% fpse_weekDay$weekday)] -> missing_category_days
is_empty(missing_category_days) -> test

as.data.frame(fpse_weekDay) -> fpse_weekDay

if(test == FALSE) {
   add_row(fpse_weekDay, weekday = missing_category_days) -> fpse_weekDay
}

fpse_weekDay %>% 
  replace(., is.na(.), 0) %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Day of the Week" = weekday) -> fpse_weekDay

monthCrimes20 %>%
  filter(., neighborhood == 39) %>%
  group_by(violent, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Crimes Against Persons" = violent) -> fpse_violent

monthCrimes20 %>%
  filter(., neighborhood == 39) %>%
  group_by(dayNight, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Time of Day" = dayNight) -> fpse_dayNight

```

```{r FPSE Flextables Knit, echo = FALSE}
flextable(fpse_crimeCat) %>%
  autofit() -> flex01

flextable(fpse_weekDay) %>%
  colformat_num(., digits = 0) %>%
  autofit() -> flex02

flextable(fpse_violent) %>%
  autofit() -> flex03

flextable(fpse_dayNight) %>%
  autofit() -> flex04

# add to powerpoint
report%>%
  add_slide()%>%
  ph_with("Forest Park Southeast: Summary Tables", 
               location = ph_location_type(
                 type = "title"))%>%
  phl_with_flextable(olay = offlayout, 4, flex01)%>%
  phl_with_flextable(olay = offlayout, 2, flex02)%>%
  phl_with_flextable(olay = offlayout, 3, flex03)%>%
  phl_with_flextable(olay = offlayout, 5, flex04) -> report
```

## Forest Park Southeast: Total Crime Map

```{r FPSE color palette, include = FALSE}
sub <- filter(monthCrimes20_sf, neighborhood == 39)
col <- character(0)
if("Aggravated Assault" %in% sub$crimeCatName){col <- c("Aggravated Assault" = "#e41a1c")}
if("Arson" %in% sub$crimeCatName){col <- c(col, "Arson" = "#A65628")}
if("Burgalry" %in% sub$crimeCatName){col <- c(col, "Burgalry" = "#377eb8")}
if("Homicide" %in% sub$crimeCatName){col <- c(col, "Homicide" = "#FFFF33")}
if("Larceny" %in% sub$crimeCatName){col <- c(col, "Larceny" = "#4DAF4A")}
if("Motor Vehicle Theft" %in% sub$crimeCatName){col <- c(col, "Motor Vehicle Theft" = "#984EA3")}
if("Robbery" %in% sub$crimeCatName){col <- c(col, "Robbery" = "#FF7F00")}
```

```{r FPSE Total Crime Prep, include = FALSE}
tm_shape(fpse_tiles) +
  tm_rgb() +
  nhoods_sf %>%
  filter(., neighborhood == 39) %>%
  tm_shape() +
    tm_fill(col = "#9ecae1",
            alpha = .5) +
    tm_borders(col = "black",
               lwd = 2,
               lty = "dashed") +
  filter(monthCrimes20_sf,
         neighborhood == 39) %>%
  tm_shape() +
    tm_bubbles(size = .25,
               col = "crimeCatName",
               palette = col,
               title.col = "Part 1 Crimes") +
  tm_credits("© Mapbox, © OpenStreetMap", position = c("left", "BOTTOM")) +
  tm_layout(
    frame = FALSE,
    legend.bg.color = "white",
    legend.frame=TRUE,
    legend.outside = TRUE,
    legend.position = c("right", "bottom")) -> fpse_total_tm

tmap_save(fpse_total_tm, file = here("results", params$year, params$month, "fpse", "fpse_total_tm.jpeg"), width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "fpse", "fpse_total_tm.jpeg"), width = 9, height = 5), location = ph_location_type(type = "body"), use_loc_size = FALSE)%>%
  ph_with("Forest Park Southeast: Total Crime Map", 
               location = ph_location_type(
                 type = "title") )-> report
```

## Botanical Heights: Summary Notes

```{r BOT Summary Prep, include=FALSE}
tc19 <- nrow(monthCrimes19[monthCrimes19$neighborhood == 28,])
tc20 <- nrow(monthCrimes20[monthCrimes20$neighborhood == 28,])
cap19 <- nrow(monthCrimes19[monthCrimes19$neighborhood == 28 & monthCrimes19$crimeCatNum == 4 | monthCrimes19$neighborhood == 28 & monthCrimes19$crimeCatNum == 3,])
cap20 <- nrow(monthCrimes20[monthCrimes20$neighborhood == 28 & monthCrimes20$crimeCatNum == 4 | monthCrimes20$neighborhood == 28 & monthCrimes20$crimeCatNum == 3,])

tc_ytd19 <- nrow(ytdCrimes19[ytdCrimes19$neighborhood == 28,])
tc_ytdCurrent <- nrow(ytdCrimes20[ytdCrimes20$neighborhood == 28,])
cap19_ytd <- nrow(ytdCrimes19[ytdCrimes19$neighborhood == 28 & ytdCrimes19$crimeCatNum == 4 | ytdCrimes19$neighborhood == 28 & ytdCrimes19$crimeCatNum == 3,])
cap20_ytd <- nrow(ytdCrimes20[ytdCrimes20$neighborhood == 28 & ytdCrimes20$crimeCatNum == 4 | ytdCrimes20$neighborhood == 28 & ytdCrimes20$crimeCatNum == 3,])

pct_chg_mth1 <- (tc20 - tc19)/tc19
pct_chg_mth <- percent(pct_chg_mth1)
if(is.nan(pct_chg_mth1)){pct_chg_mth[is.nan(pct_chg_mth1)] <- 0}
if(is.infinite(pct_chg_mth1)){pct_chg_mth[is.infinite(pct_chg_mth1)] <- "Infinite"}

pct_chg_cap1 <- (cap20 - cap19)/cap19
pct_chg_cap <- percent(pct_chg_cap1)
if(is.nan(pct_chg_cap1)){pct_chg_cap[is.nan(pct_chg_cap1)] <- 0}
if(is.infinite(pct_chg_cap1)){pct_chg_cap[is.infinite(pct_chg_cap1)] <- "Infinite"}

pct_chg_ytd1 <- (tc_ytdCurrent - tc_ytd19)/tc_ytd19
pct_chg_ytd <- percent(pct_chg_ytd1)
if(is.nan(pct_chg_ytd1)){pct_chg_ytd[is.nan(pct_chg_ytd1)] <- 0}
if(is.infinite(pct_chg_ytd1)){pct_chg_ytd[is.infinite(pct_chg_ytd1)] <- "Infinite"}

pct_chg_ytd_cap1 <- (cap20_ytd - cap19_ytd)/cap19_ytd
pct_chg_ytd_cap <- percent(pct_chg_ytd_cap1)
if(is.nan(pct_chg_ytd_cap1)){pct_chg_ytd_cap[is.nan(pct_chg_ytd_cap1)] <- 0}
if(is.infinite(pct_chg_ytd_cap1)){pct_chg_ytd_cap[is.infinite(pct_chg_ytd_cap1)] <- "Infinite"}

sprint_1 <- sprintf("%s total crimes in %s %s", 
                    tc20, params$month, params$year)
sprint_2 <- sprintf("%s total crimes in %s", 
                    tc_ytdCurrent, params$year)

# text formatting
color24a <- fp_text(color = ifelse(pct_chg_mth1 == 0, "#00B0F0", ifelse(pct_chg_mth < 0, "#00B050", "red")), font.size = 24)
color20a <- fp_text(color = ifelse(pct_chg_cap1 == 0, "#00B0F0", ifelse(pct_chg_cap < 0, "#00B050", "red")), font.size = 20)
color24b <- fp_text(color = ifelse(pct_chg_ytd1 == 0, '#00B0F0', ifelse(pct_chg_ytd < 0, '#00B050', 'red')), font.size = 24)
color20b <- fp_text(color = ifelse(pct_chg_ytd_cap1 == 0, "#00B0F0", ifelse(pct_chg_ytd_cap < 0, "#00B050", "red")), font.size = 20)
  
# create summary notes
summary <- block_list(
  fpar(ftext(sprint_1, boldline)),
  fpar(ftext(paste(pct_chg_mth, "change ", sep = " "), color24a),
       ftext(paste("compared to ", params$month, " ", params$pastyear, " (", tc19, " total crimes)", sep = ""), reg24)),
  fpar(ftext(paste(cap20, "crime(s) against persons", sep = " "), bold),
       ftext(paste(" in", params$month, params$year, sep = " "), reg24)),
  fpar(ftext(paste(pct_chg_cap, "change", sep = " "), color20a),
       ftext(paste(" compared to ", params$month, " ", params$pastyear, " (", cap19, " crimes against persons)", sep = ""), reg20)),
  fpar(ftext(sprint_2, boldline)),
  fpar(ftext(paste(pct_chg_ytd, "change ", sep = " "), color24b),
       ftext(paste("compared to this time in ", params$pastyear, " (", tc_ytd19, " total crimes)", sep = ""), reg24)),
  fpar(ftext(paste(cap20_ytd, "crime(s) against persons", sep = " "), bold),
       ftext(paste(" in", params$year, sep = " "), reg24)),
  fpar(ftext(paste(pct_chg_ytd_cap, "change", sep = " "), color20b),
       ftext(paste(" compared to this time in ", params$pastyear, " (", cap19_ytd, " crimes against persons)", sep = ""), reg20))
)

# write summary notes to powerpoint slide
report%>%
  add_slide(layout = 'Title and Content', master = 'Office Theme')%>%
  ph_with(value = "Botanical Heights: Summary Notes", location = ph_location_type(type = "title"))%>%
  ph_with(summary, location = ph_location_type(type = "body"), is_list = TRUE, level_list = c(1, 2, 2, 3, 1, 2, 2, 3)) -> report
```

## Botanical Heights: Year to Year Comparison

```{r BOT Year Comps Prep, include=FALSE}
totalCrimes19 %>%
  filter(., neighborhood == 28) %>%
  group_by(monthVar, .drop = FALSE) %>%
  count(crimeCatName) %>%
  rename(., "Number of Crimes" = n) %>%
  pivot_wider(names_from = monthVar, values_from = "Number of Crimes") %>%
  replace(., is.na(.), 0) -> bot_2019

ytdCrimes20 %>%
  filter(., neighborhood == 28) %>%
  group_by(monthVar) %>%
  count(crimeCatName) %>%
  rename(., "Number of Crimes" = n) %>%
  pivot_wider(names_from = monthVar, values_from = "Number of Crimes") %>%
  replace(., is.na(.), 0) -> bot_2020
```


```{r BOT Total Crimes Flextable 2019, echo = FALSE}
part1crimes[!(part1crimes %in% bot_2019$crimeCatName)] -> missing_category
is_empty(missing_category) -> test

if(test == FALSE) {
   add_row(bot_2019, crimeCatName = missing_category) -> bot_2019
}

bot_2019 %>% 
  arrange(., crimeCatName) %>%
  replace(., is.na(.), 0) %>%
  adorn_totals(., "col", name = "Total") %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Part 1 Crimes" = crimeCatName) -> bot_2019

flextable(bot_2019) %>%
  colformat_num(.,  digits = 0) %>%
  colformat_num(.,  digits = 0) %>%
  add_header_lines(values = params$pastyear)%>%
  autofit() -> flex
```

```{r BOT Total Crimes Flextable 2020, echo = FALSE}
part1crimes[!(part1crimes %in% bot_2020$crimeCatName)] -> missing_category
is_empty(missing_category) -> test

if(test == FALSE) {
   add_row(bot_2020, crimeCatName = missing_category) -> bot_2020
}

bot_2020 %>% 
  arrange(., crimeCatName) %>%
  replace(., is.na(.), 0) %>%
  adorn_totals(., "col", name = "Total") %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Part 1 Crimes" = crimeCatName) -> bot_2020

flextable(bot_2020) %>%
  colformat_num(., digits = 0) %>%
  colformat_num(., digits = 0) %>%
  add_header_lines(values = params$year)%>%
  autofit() -> flex01

# add powerpoint slide
report%>%
  add_slide()%>%
  phl_with_text(olay = offlayout01, 1, "Botanical Heights: Year to Year Comparison")%>%
  phl_with_flextable(olay = offlayout01, 2, flex)%>%
  phl_with_flextable(olay = offlayout01, 3, flex01) -> report
```

## Botanical Heights: Summary Tables

```{r BOT Tables Prep, include = FALSE}
monthCrimes20 %>%
  filter(., neighborhood == 28) %>%
  group_by(crimeCatName, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Part 1 Crimes" = crimeCatName) -> bot_crimeCat

monthCrimes20 %>%
  filter(., neighborhood == 28) %>%
  group_by(weekday, .drop = FALSE) %>%
  count() %>%
  rename(., "Number of Crimes" = n) %>%
  replace(., is.na(.), 0) -> bot_weekDay

wkdys[!(wkdys %in% bot_weekDay$weekday)] -> missing_category_days
is_empty(missing_category_days) -> test

as.data.frame(bot_weekDay) -> bot_weekDay

if(test == FALSE) {
   add_row(bot_weekDay, weekday = missing_category_days) -> bot_weekDay
}

bot_weekDay %>% 
  replace(., is.na(.), 0) %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Day of the Week" = weekday) -> bot_weekDay

monthCrimes20 %>%
  filter(., neighborhood == 28) %>%
  group_by(violent, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Crimes Against Persons" = violent) -> bot_violent


monthCrimes20 %>%
  filter(., neighborhood == 28) %>%
  group_by(dayNight, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Time of Day" = dayNight) -> bot_dayNight
```

```{r BOT Flextables Knit, echo = FALSE}
flextable(bot_crimeCat) %>%
  autofit() -> flex01

flextable(bot_weekDay) %>%
  colformat_num(.,  digits = 0) %>%
  autofit() -> flex02

flextable(bot_violent) %>%
  autofit() -> flex03

flextable(bot_dayNight) %>%
  autofit() -> flex04

# add to powerpoint
report%>%
  add_slide()%>%
  ph_with("Botanical Heights: Summary Tables", 
               location = ph_location_type(
                 type = "title"))%>%
  phl_with_flextable(olay = offlayout, 4, flex01)%>%
  phl_with_flextable(olay = offlayout, 2, flex02)%>%
  phl_with_flextable(olay = offlayout, 3, flex03)%>%
  phl_with_flextable(olay = offlayout, 5, flex04) -> report
```

## Botanical Heights: Total Crime Map

```{r BOT color palette, include = FALSE}
sub <- filter(monthCrimes20_sf, neighborhood == 28)
col <- character(0)
if("Aggravated Assault" %in% sub$crimeCatName){col <- c("Aggravated Assault" = "#e41a1c")}
if("Arson" %in% sub$crimeCatName){col <- c(col, "Arson" = "#A65628")}
if("Burgalry" %in% sub$crimeCatName){col <- c(col, "Burgalry" = "#377eb8")}
if("Homicide" %in% sub$crimeCatName){col <- c(col, "Homicide" = "#FFFF33")}
if("Larceny" %in% sub$crimeCatName){col <- c(col, "Larceny" = "#4DAF4A")}
if("Motor Vehicle Theft" %in% sub$crimeCatName){col <- c(col, "Motor Vehicle Theft" = "#984EA3")}
if("Robbery" %in% sub$crimeCatName){col <- c(col, "Robbery" = "#FF7F00")}
```

```{r BOT Total Crime Prep, include = FALSE}
tm_shape(bot_tiles) +
  tm_rgb() +
  nhoods_sf %>%
  filter(., neighborhood == 28) %>%
  tm_shape() +
    tm_fill(col = "#9ecae1",
            alpha = .5) +
    tm_borders(col = "black",
               lwd = 2,
               lty = "dashed") +
  filter(monthCrimes20_sf,
         neighborhood == 28) %>%
  tm_shape() +
    tm_bubbles(size = .25,
               col = "crimeCatName",
               palette = col,
               title.col = "Part 1 Crimes") +
  tm_credits("© Mapbox, © OpenStreetMap", position = c("left", "BOTTOM")) +
  tm_layout(
    frame = FALSE,
    legend.bg.color = "white",
    legend.frame=TRUE,
    legend.outside = TRUE,
    legend.position = c("right", "bottom")) -> bot_total_tm

tmap_save(bot_total_tm, file = here("results", params$year, params$month, "bot", "bot_total_crimes.jpeg"), width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "bot", "bot_total_crimes.jpeg"), width = 9, height = 5), location = ph_location_type(type = "body"), use_loc_size = FALSE)%>%
  ph_with("Botanical Heights: Total Crime Map", 
               location = ph_location_type(
                 type = "title") )-> report
```

## Botanical Heights: Crime by Days of the Week

```{r BOT Crime by Weekday - Graph Prep, include = FALSE}
monthCrimes20 %>%
  filter(., neighborhood == 28) %>%
  group_by(weekday, .drop = FALSE) %>%
  count() %>%
  replace(., is.na(.), 0) -> bot_weekDay

wkdys[!(wkdys %in% bot_weekDay$weekday)] -> missing_category_days
is_empty(missing_category_days) -> test

as.data.frame(bot_weekDay) -> bot_weekDay

if(test == FALSE) {
   add_row(bot_weekDay, weekday = missing_category_days) -> bot_weekDay
}

  ggplot(bot_weekDay, aes(x=weekday, y=n, group = 1)) +
    geom_line(color="blue") +
    geom_point() +
    xlab("Day of Week") + ylab("Total Crimes")

ggsave(here("results", params$year, params$month, "bot", "bot_crime_weekday_graph.jpeg"), dpi = 500)

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "bot", "bot_crime_weekday_graph.jpeg"), width = 9, height = 5.45),
          location = ph_location_type(type = "body"), use_loc_size = FALSE)%>%
  ph_with("Botanical Heights: Crime by Days of the Week", 
               location = ph_location_type(
                 type = "title") )-> report
```

## District 2: Crime Rates Map

```{r District 2 Density Maps Prep, include = FALSE}
dst2_rateMap <- tm_shape(dst2_tiles) +
  tm_rgb() +
  tm_shape(dst_2_pop_sf) +
  tm_polygons(col = "crimeRate",
              palette = "BuPu",
              style = "jenks",
              title = "Crimes per 1,000 Residents") +
  tm_text("neighborhood", shadow=TRUE) +
  tm_layout(
    frame = FALSE,
    legend.bg.color = "white",
    legend.frame=TRUE,
    legend.outside = TRUE,
    legend.position = c("right", "bottom"))

tmap_save(dst2_rateMap, file = here("results", params$year, params$month, "district-2", "dst2_rates.jpeg"), width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "district-2", "dst2_rates.jpeg"), width = 9, height = 5),
          location = ph_location_type(type = "body"), use_loc_size = FALSE)%>%
  ph_with("District 2: Crime Rates Map", 
               location = ph_location_type(
                 type = "title") )-> report
```

## District 2: Density Map Explanation

```{r District 2 Density Map Explanation Prep, include = FALSE}
library(qwraps2)
options(qwraps2_markup = "markdown")

dst_2_pop_sf <- as.data.frame(dst_2_pop_sf)
summary_statistics <-
  list(
    "Crime Rates" =
      list(
        "mean" = ~mean(crimeRate, na_rm = TRUE),
        "min" = ~min(crimeRate, na.rm = TRUE),
        "max" = ~max(crimeRate, na.rm = TRUE)),
    "Crime Total" =
      list(
        "mean" = ~mean(crimeTotal, na_rm = TRUE),
        "min" = ~min(crimeTotal, na.rm = TRUE),
        "max" = ~max(crimeTotal, na.rm = TRUE)))

dst_2_table <- summary_table(dst_2_pop_sf, summary_statistics)

print(dst_2_table,
      cnames = "Summary Statistics")

dst_2_rate_mean <- mean(dst_2_pop_sf$crimeRate)
dst_2_rate_mean

dst_2_min <- dst_2_pop_sf[which.min(dst_2_pop_sf$crimeRate),]
dst_2_min_rate_nhd <- print(dst_2_min$NHD_NAME, max.levels = 0)
dst_2_min_rate <- print(dst_2_min$crimeRate, max.levels = 0)

dst_2_max <- dst_2_pop_sf[which.max(dst_2_pop_sf$crimeRate),]
dst_2_max_rate_nhd <- print(dst_2_max$NHD_NAME, max.levels = 0)
dst_2_max_rate <- print(dst_2_max$crimeRate, max.levels = 0)

dst_2_total_mean <- mean(dst_2_pop_sf$crimeTotal)
dst_2_total_mean

dst_2_minT <- dst_2_pop_sf[which.min(dst_2_pop_sf$crimeTotal),]
dst_2_min_tot_nhd <- print(dst_2_minT$NHD_NAME, max.levels = 0)
dst_2_min_tot <- print(dst_2_minT$crimeTotal, max.levels = 0)

dst_2_maxT <- dst_2_pop_sf[which.max(dst_2_pop_sf$crimeTotal),]
dst_2_max_tot_nhd <- print(dst_2_maxT$NHD_NAME, max.levels = 0)
dst_2_max_tot <- print(dst_2_maxT$crimeTotal, max.levels = 0)

# add to powerpoint
report%>%
    add_slide(layout = 'Title and Content', master = 'Office Theme')%>%
    ph_with(value = "District 2: Density Map Explanation", location = ph_location_type(type = "title"))%>%
    ph_with(block_list(fpar(ftext("There are 23 neighborhoods in District 2. The South Hampton neighborhood is split between District 2 and District 1.", fp_text(color = "black", font.size = 24)))), location = ph_location_type(type = "body"))%>%
    ph_add_par()%>%
    ph_add_text(str = paste("in one neighborhood was ", dst_2_min_tot, " (", dst_2_min_tot_nhd, ")", sep = ""), style = fp_text(color = "black", font.size = 22)) %>%
    ph_add_text(str = "The minimum number of crimes ", 
                style = fp_text(color = "#00B050", font.size = 22))%>%
    ph_add_par()%>%
    ph_add_text(str = paste("in one neighborhood was ", dst_2_max_tot, " (", dst_2_max_tot_nhd, ")", sep = ""), style = fp_text(color = "black", font.size = 22))%>%
    ph_add_text(str = "The maximum number of crimes ",
                style = fp_text(color = "red", font.size = 22))%>%
    ph_add_par()%>%
    ph_add_text(str = paste("in one neighborhood was", round(dst_2_total_mean, digits = 2), 
                            sep = " "), style = fp_text(color = "black", font.size = 22))%>%
    ph_add_text(str = "The mean number of crimes ",
                style = fp_text(color = "#00B0F0", font.size = 22))%>%
    ph_add_par()%>%
    ph_add_text(str = paste("in one neighborhood was ", round(dst_2_min_rate, digits = 2), " (", dst_2_min_rate_nhd, ")", sep = ""),
                style = fp_text(color = "black", font.size = 22))%>%
    ph_add_text(str = "The minimum rate of crimes ",
                style = fp_text(color = "#00B050", font.size = 22))%>%
    ph_add_par()%>%
    ph_add_text(str = paste("in one neighborhood was ", round(dst_2_max_rate, digits = 2), " (", dst_2_max_rate_nhd, ")", sep = ""),
                style = fp_text(color = "black", font.size = 22))%>%
    ph_add_text(str = "The maximum rate of crimes ",
                style = fp_text(color = "red", font.size = 22))%>%
    ph_add_par()%>%
    ph_add_text(str = paste("in one neighborhood was", round(dst_2_rate_mean, digits = 2), 
                            sep = " "), style = fp_text(color = "black", font.size = 22))%>%
    ph_add_text(str = "The mean rate of crimes ",
                style = fp_text(color = "#00B0F0", font.size = 22)) -> report
```

## Summary Notes: Central West End

```{r CWE Summary Notes Prep, include=FALSE}
tc19 <- nrow(monthCrimes19[monthCrimes19$neighborhood == 38,])
tc20 <- nrow(monthCrimes20[monthCrimes20$neighborhood == 38,])
cap19 <- nrow(monthCrimes19[monthCrimes19$neighborhood == 38 & monthCrimes19$crimeCatNum == 4 | monthCrimes19$neighborhood == 38 & monthCrimes19$crimeCatNum == 3,])
cap20 <- nrow(monthCrimes20[monthCrimes20$neighborhood == 38 & monthCrimes20$crimeCatNum == 4 | monthCrimes20$neighborhood == 38 & monthCrimes20$crimeCatNum == 3,])

tc_ytd19 <- nrow(ytdCrimes19[ytdCrimes19$neighborhood == 38,])
tc_ytdCurrent <- nrow(ytdCrimes20[ytdCrimes20$neighborhood == 38,])
cap19_ytd <- nrow(ytdCrimes19[ytdCrimes19$neighborhood == 38 & ytdCrimes19$crimeCatNum == 4 | ytdCrimes19$neighborhood == 38 & ytdCrimes19$crimeCatNum == 3,])
cap20_ytd <- nrow(ytdCrimes20[ytdCrimes20$neighborhood == 38 & ytdCrimes20$crimeCatNum == 4 | ytdCrimes20$neighborhood == 38 & ytdCrimes20$crimeCatNum == 3,])

pct_chg_mth1 <- (tc20 - tc19)/tc19
pct_chg_mth <- percent(pct_chg_mth1)
if(is.nan(pct_chg_mth1)){pct_chg_mth[is.nan(pct_chg_mth1)] <- 0}
if(is.infinite(pct_chg_mth1)){pct_chg_mth[is.infinite(pct_chg_mth1)] <- "Infinite"}

pct_chg_cap1 <- (cap20 - cap19)/cap19
pct_chg_cap <- percent(pct_chg_cap1)
if(is.nan(pct_chg_cap1)){pct_chg_cap[is.nan(pct_chg_cap1)] <- 0}
if(is.infinite(pct_chg_cap1)){pct_chg_cap[is.infinite(pct_chg_cap1)] <- "Infinite"}

pct_chg_ytd1 <- (tc_ytdCurrent - tc_ytd19)/tc_ytd19
pct_chg_ytd <- percent(pct_chg_ytd1)
if(is.nan(pct_chg_ytd1)){pct_chg_ytd[is.nan(pct_chg_ytd1)] <- 0}
if(is.infinite(pct_chg_ytd1)){pct_chg_ytd[is.infinite(pct_chg_ytd1)] <- "Infinite"}

pct_chg_ytd_cap1 <- (cap20_ytd - cap19_ytd)/cap19_ytd
pct_chg_ytd_cap <- percent(pct_chg_ytd_cap1)
if(is.nan(pct_chg_ytd_cap1)){pct_chg_ytd_cap[is.nan(pct_chg_ytd_cap1)] <- 0}
if(is.infinite(pct_chg_ytd_cap1)){pct_chg_ytd_cap[is.infinite(pct_chg_ytd_cap1)] <- "Infinite"}

sprint_1 <- sprintf("%s total crimes in %s %s", 
                    tc20, params$month, params$year)
sprint_2 <- sprintf("%s total crimes in %s", 
                    tc_ytdCurrent, params$year)

# text formatting
color24a <- fp_text(color = ifelse(pct_chg_mth1 == 0, "#00B0F0", ifelse(pct_chg_mth < 0, "#00B050", "red")), font.size = 24)
color20a <- fp_text(color = ifelse(pct_chg_cap1 == 0, "#00B0F0", ifelse(pct_chg_cap < 0, "#00B050", "red")), font.size = 20)
color24b <- fp_text(color = ifelse(pct_chg_ytd1 == 0, '#00B0F0', ifelse(pct_chg_ytd < 0, '#00B050', 'red')), font.size = 24)
color20b <- fp_text(color = ifelse(pct_chg_ytd_cap1 == 0, "#00B0F0", ifelse(pct_chg_ytd_cap < 0, "#00B050", "red")), font.size = 20)

# create summary notes
summary <- block_list(
  fpar(ftext(sprint_1, boldline)),
  fpar(ftext(paste(pct_chg_mth, "change ", sep = " "), color24a),
       ftext(paste("compared to ", params$month, " ", params$pastyear, " (", tc19, " total crimes)", sep = ""), reg24)),
  fpar(ftext(paste(cap20, "crime(s) against persons", sep = " "), bold),
       ftext(paste(" in", params$month, params$year, sep = " "), reg24)),
  fpar(ftext(paste(pct_chg_cap, "change", sep = " "), color20a),
       ftext(paste(" compared to ", params$month, " ", params$pastyear, " (", cap19, " crimes against persons)", sep = ""), reg20)),
  fpar(ftext(sprint_2, boldline)),
  fpar(ftext(paste(pct_chg_ytd, "change ", sep = " "), color24b),
       ftext(paste("compared to this time in ", params$pastyear, " (", tc_ytd19, " total crimes)", sep = ""), reg24)),
  fpar(ftext(paste(cap20_ytd, "crime(s) against persons", sep = " "), bold),
       ftext(paste(" in", params$year, sep = " "), reg24)),
  fpar(ftext(paste(pct_chg_ytd_cap, "change", sep = " "), color20b),
       ftext(paste(" compared to this time in ", params$pastyear, " (", cap19_ytd, " crimes against persons)", sep = ""), reg20))
)

# write summary notes to powerpoint slide
report%>%
  add_slide(layout = 'Title and Content', master = 'Office Theme')%>%
  ph_with(value = "Central West End: Summary Notes", location = ph_location_type(type = "title"))%>%
  ph_with(summary, location = ph_location_type(type = "body"), is_list = TRUE, level_list = c(1, 2, 2, 3, 1, 2, 2, 3)) -> report
```

## Central West End: Year to Year Comparison

```{r CWE Year Comps Prep,include=FALSE}
totalCrimes19 %>%
  filter(., neighborhood == 38) %>%
  group_by(monthVar, .drop = FALSE) %>%
  count(crimeCatName) %>%
  rename(., "Number of Crimes" = n) %>%
  pivot_wider(names_from = monthVar, values_from = "Number of Crimes") %>%
  replace(., is.na(.), 0) -> cwe_2019

ytdCrimes20 %>%
  filter(., neighborhood == 38) %>%
  group_by(monthVar) %>%
  count(crimeCatName) %>%
  rename(., "Number of Crimes" = n) %>%
  pivot_wider(names_from = monthVar, values_from = "Number of Crimes") %>%
  replace(., is.na(.), 0) -> cwe_2020
```

```{r CWE Total Crimes Flextable 2019, echo = FALSE}
part1crimes[!(part1crimes %in% cwe_2019$crimeCatName)] -> missing_category
is_empty(missing_category) -> test

if(test == FALSE) {
   add_row(cwe_2019, crimeCatName = missing_category) -> cwe_2019
}

cwe_2019 %>% 
  arrange(., crimeCatName) %>%
  replace(., is.na(.), 0) %>%
  adorn_totals(., "col", name = "Total") %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Part 1 Crimes" = crimeCatName) -> cwe_2019

flextable(cwe_2019) %>%
  colformat_num(., digits = 0) %>%
  colformat_num(., digits = 0) %>%
  add_header_lines(values = params$pastyear)%>%
  autofit() -> flex
```

```{r CWE Total Crimes Flextable 2020, echo = FALSE}
part1crimes[!(part1crimes %in% cwe_2020$crimeCatName)] -> missing_category
is_empty(missing_category) -> test

if(test == FALSE) {
   add_row(cwe_2020, crimeCatName = missing_category) -> cwe_2020
}

cwe_2020 %>% 
  arrange(., crimeCatName) %>%
  replace(., is.na(.), 0) %>%
  adorn_totals(., "col", name = "Total") %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Part 1 Crimes" = crimeCatName) -> cwe_2020

flextable(cwe_2020) %>%
  colformat_num(., digits = 0) %>%
  colformat_num(., digits = 0) %>%
  add_header_lines(values = params$year)%>%
  autofit() -> flex01

# add powerpoint slide
report%>%
  add_slide()%>%
  phl_with_text(olay = offlayout01, 1, "Central West End: Year to Year Comparison")%>%
  phl_with_flextable(olay = offlayout01, 2, flex)%>%
  phl_with_flextable(olay = offlayout01, 3, flex01) -> report
```

## Central West End: Summary Tables

```{r CWE Tables Prep, include = FALSE}
monthCrimes20 %>%
  filter(., neighborhood == 38) %>%
  group_by(crimeCatName, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Part 1 Crimes" = crimeCatName) -> cwe_crimeCat

monthCrimes20 %>%
  filter(., neighborhood == 38) %>%
  group_by(weekday, .drop = FALSE) %>%
  count() %>%
  rename(., "Number of Crimes" = n) %>%
  replace(., is.na(.), 0) -> cwe_weekDay

wkdys[!(wkdys %in% cwe_weekDay$weekday)] -> missing_category_days
is_empty(missing_category_days) -> test

as.data.frame(cwe_weekDay) -> cwe_weekDay

if(test == FALSE) {
   add_row(cwe_weekDay, weekday = missing_category_days) -> cwe_weekDay
}

cwe_weekDay %>% 
  replace(., is.na(.), 0) %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Day of the Week" = weekday) -> cwe_weekDay

monthCrimes20 %>%
  filter(., neighborhood == 38) %>%
  group_by(violent, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Crimes Against Persons" = violent) -> cwe_violent

monthCrimes20 %>%
  filter(., neighborhood == 38) %>%
  group_by(dayNight, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Time of Day" = dayNight) -> cwe_dayNight

```

```{r CWE Flextables Knit, echo = FALSE}
flextable(cwe_crimeCat) %>%
  autofit() -> flex01

flextable(cwe_weekDay) %>%
  colformat_num(., digits = 0) %>%
  autofit() -> flex02

flextable(cwe_violent) %>%
  autofit() -> flex03

flextable(cwe_dayNight) %>%
  autofit() -> flex04

# add to powerpoint
report%>%
  add_slide()%>%
  ph_with("Central West End: Summary Tables", 
               location = ph_location_type(
                 type = "title"))%>%
  phl_with_flextable(olay = offlayout, 4, flex01)%>%
  phl_with_flextable(olay = offlayout, 2, flex02)%>%
  phl_with_flextable(olay = offlayout, 3, flex03)%>%
  phl_with_flextable(olay = offlayout, 5, flex04) -> report
```

## Central West End: Total Crime Map

```{r CWE color palette, include = FALSE}
sub <- filter(monthCrimes20_sf, neighborhood == 38)
col <- character(0)
if("Aggravated Assault" %in% sub$crimeCatName){col <- c("Aggravated Assault" = "#e41a1c")}
if("Arson" %in% sub$crimeCatName){col <- c(col, "Arson" = "#A65628")}
if("Burgalry" %in% sub$crimeCatName){col <- c(col, "Burgalry" = "#377eb8")}
if("Homicide" %in% sub$crimeCatName){col <- c(col, "Homicide" = "#FFFF33")}
if("Larceny" %in% sub$crimeCatName){col <- c(col, "Larceny" = "#4DAF4A")}
if("Motor Vehicle Theft" %in% sub$crimeCatName){col <- c(col, "Motor Vehicle Theft" = "#984EA3")}
if("Robbery" %in% sub$crimeCatName){col <- c(col, "Robbery" = "#FF7F00")}
```

```{r CWE Total Crime Prep, include = FALSE}
tm_shape(cwe_tiles) +
  tm_rgb() +
  nhoods_sf %>%
  filter(., neighborhood == 38) %>%
  tm_shape() +
    tm_fill(col = "#9ecae1",
            alpha = .5) +
    tm_borders(col = "black",
               lwd = 2,
               lty = "dashed") +
  filter(monthCrimes20_sf,
         neighborhood == 38) %>%
  tm_shape() +
    tm_bubbles(size = .25,
               col = "crimeCatName",
               palette = col,
               title.col = "Part 1 Crimes") +
  tm_credits("© Mapbox, © OpenStreetMap", position = c("left", "BOTTOM")) +
  tm_layout(
    frame = FALSE,
    legend.bg.color = "white",
    legend.frame=TRUE,
    legend.outside = TRUE,
    legend.position = c("right", "bottom")) -> cwe_total_tm

tmap_save(cwe_total_tm, file = here("results", params$year, params$month, "cwe", "cwe_total_crimes.jpeg"), width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "cwe", "cwe_total_crimes.jpeg"), width = 9, height = 5), location = ph_location_type(type="body"), use_loc_size = FALSE)%>%
  ph_with("Central West End: Total Crime Map", 
               location = ph_location_type(
                 type = "title") )-> report
```

## Washington University Medical Campus: Summary Notes

```{r WUMC Summary Prep, include=FALSE}
tc19 <- nrow(mc_crimes_month19)
tc20 <- nrow(mc_crimes_month20)
cap19 <- nrow(mc_crimes_month19[mc_crimes_month19$crimeCatNum == 4 | mc_crimes_month19$crimeCatNum == 3,])
cap20 <- nrow(mc_crimes_month20[mc_crimes_month20$crimeCatNum == 4 | mc_crimes_month20$crimeCatNum == 3,])

tc_ytd19 <- nrow(mc_crimes_ytd19)
tc_ytdCurrent <- nrow(mc_crimes_ytd20)
cap19_ytd <- nrow(mc_crimes_ytd19[mc_crimes_ytd19$crimeCatNum == 4 | mc_crimes_ytd19$crimeCatNum == 3,])
cap20_ytd <- nrow(mc_crimes_ytd20[mc_crimes_ytd20$crimeCatNum == 4 | mc_crimes_ytd20$crimeCatNum == 3,])

pct_chg_mth1 <- (tc20 - tc19)/tc19
pct_chg_mth <- percent(pct_chg_mth1)
if(is.nan(pct_chg_mth1)){pct_chg_mth[is.nan(pct_chg_mth1)] <- 0}
if(is.infinite(pct_chg_mth1)){pct_chg_mth[is.infinite(pct_chg_mth1)] <- "Infinite"}

pct_chg_cap1 <- (cap20 - cap19)/cap19
pct_chg_cap <- percent(pct_chg_cap1)
if(is.nan(pct_chg_cap1)){pct_chg_cap[is.nan(pct_chg_cap1)] <- 0}
if(is.infinite(pct_chg_cap1)){pct_chg_cap[is.infinite(pct_chg_cap1)] <- "Infinite"}

pct_chg_ytd1 <- (tc_ytdCurrent - tc_ytd19)/tc_ytd19
pct_chg_ytd <- percent(pct_chg_ytd1)
if(is.nan(pct_chg_ytd1)){pct_chg_ytd[is.nan(pct_chg_ytd1)] <- 0}
if(is.infinite(pct_chg_ytd1)){pct_chg_ytd[is.infinite(pct_chg_ytd1)] <- "Infinite"}

pct_chg_ytd_cap1 <- (cap20_ytd - cap19_ytd)/cap19_ytd
pct_chg_ytd_cap <- percent(pct_chg_ytd_cap1)
if(is.nan(pct_chg_ytd_cap1)){pct_chg_ytd_cap[is.nan(pct_chg_ytd_cap1)] <- 0}
if(is.infinite(pct_chg_ytd_cap1)){pct_chg_ytd_cap[is.infinite(pct_chg_ytd_cap1)] <- "Infinite"}

sprint_1 <- sprintf("%s total crimes in %s %s", 
                    tc20, params$month, params$year)
sprint_2 <- sprintf("%s total crimes in %s", 
                    tc_ytdCurrent, params$year)

# text formatting
color24a <- fp_text(color = ifelse(pct_chg_mth1 == 0, "#00B0F0", ifelse(pct_chg_mth < 0, "#00B050", "red")), font.size = 24)
color20a <- fp_text(color = ifelse(pct_chg_cap1 == 0, "#00B0F0", ifelse(pct_chg_cap < 0, "#00B050", "red")), font.size = 20)
color24b <- fp_text(color = ifelse(pct_chg_ytd1 == 0, '#00B0F0', ifelse(pct_chg_ytd < 0, '#00B050', 'red')), font.size = 24)
color20b <- fp_text(color = ifelse(pct_chg_ytd_cap1 == 0, "#00B0F0", ifelse(pct_chg_ytd_cap < 0, "#00B050", "red")), font.size = 20)

# create summary notes
summary <- block_list(
  fpar(ftext(sprint_1, boldline)),
  fpar(ftext(paste(pct_chg_mth, "change ", sep = " "), color24a),
       ftext(paste("compared to ", params$month, " ", params$pastyear, " (", tc19, " total crimes)", sep = ""), reg24)),
  fpar(ftext(paste(cap20, "crime(s) against persons", sep = " "), bold),
       ftext(paste(" in", params$month, params$year, sep = " "), reg24)),
  fpar(ftext(paste(pct_chg_cap, "change", sep = " "), color20a),
       ftext(paste(" compared to ", params$month, " ", params$pastyear, " (", cap19, " crimes against persons)", sep = ""), reg20)),
  fpar(ftext(sprint_2, boldline)),
  fpar(ftext(paste(pct_chg_ytd, "change ", sep = " "), color24b),
       ftext(paste("compared to this time in ", params$pastyear, " (", tc_ytd19, " total crimes)", sep = ""), reg24)),
  fpar(ftext(paste(cap20_ytd, "crime(s) against persons", sep = " "), bold),
       ftext(paste(" in", params$year, sep = " "), reg24)),
  fpar(ftext(paste(pct_chg_ytd_cap, "change", sep = " "), color20b),
       ftext(paste(" compared to this time in ", params$pastyear, " (", cap19_ytd, " crimes against persons)", sep = ""), reg20))
)

# write summary notes to powerpoint slide
report%>%
  add_slide(layout = 'Title and Content', master = 'Office Theme')%>%
  ph_with(value = "Washington University Medical Campus: Summary Notes", location = ph_location_type(type = "title"))%>%
  ph_with(summary, location = ph_location_type(type = "body"), is_list = TRUE, level_list = c(1, 2, 2, 3, 1, 2, 2, 3)) -> report
```

## Washington University Medical Campus: Year to Year Comparison

```{r WUMC Year Comps Prep, include = FALSE}
mc_crimes_total19 %>%
  group_by(monthVar, .drop = FALSE) %>%
  count(crimeCatName) %>%
  rename(., "Number of Crimes" = n) %>%
  pivot_wider(names_from = monthVar, values_from = "Number of Crimes") %>%
  replace(., is.na(.), 0)-> mc_2019

mc_crimes_ytd20 %>%
  group_by(monthVar) %>%
  count(crimeCatName) %>%
  rename(., "Number of Crimes" = n) %>%
  pivot_wider(names_from = monthVar, values_from = "Number of Crimes") %>%
  replace(., is.na(.), 0) -> mc_2020
```

```{r WUMC Total Crimes Flextable 2019, echo = FALSE}
part1crimes[!(part1crimes %in% mc_2019$crimeCatName)] -> missing_category
is_empty(missing_category) -> test

if(test == FALSE) {
   add_row(mc_2019, crimeCatName = missing_category) -> mc_2019
}

mc_2019 %>% 
  arrange(., crimeCatName) %>%
  replace(., is.na(.), 0) %>%
  adorn_totals(., "col", name = "Total") %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Part 1 Crimes" = crimeCatName) -> mc_2019

flextable(mc_2019) %>%
  colformat_num(., digits = 0) %>%
  colformat_num(., digits = 0) %>%
  add_header_lines(values = params$pastyear)%>%
  autofit() -> flex
```

```{r WUMC Total Crimes Flextable 2020, echo = FALSE}
part1crimes[!(part1crimes %in% mc_2020$crimeCatName)] -> missing_category
is_empty(missing_category) -> test

if(test == FALSE) {
   add_row(mc_2020, crimeCatName = missing_category) -> mc_2020
}

mc_2020 %>% 
  arrange(., crimeCatName) %>%
  replace(., is.na(.), 0) %>%
  adorn_totals(., "col", name = "Total") %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Part 1 Crimes" = crimeCatName) -> mc_2020

flextable(mc_2020) %>%
  colformat_num(., digits = 0) %>%
  colformat_num(., digits = 0) %>%
  add_header_lines(values = params$year)%>%
  autofit() -> flex01

# add powerpoint slide
report%>%
  add_slide()%>%
  phl_with_text(olay = offlayout01, 1, "Washington University Medical Campus: Year to Year Comparison")%>%
  phl_with_flextable(olay = offlayout01, 2, flex)%>%
  phl_with_flextable(olay = offlayout01, 3, flex01) -> report
```

## Washington University Medical Campus: Summary Tables

```{r WUMC Summary Tables Prep, include = FALSE}
mc_crimes_month20 %>%
  group_by(crimeCatName, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Part 1 Crimes" = crimeCatName) -> mc_crimeCat

mc_crimes_month20 %>%
  group_by(dayNight, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Time of Day" = dayNight) -> mc_dayNight

mc_larcenies %>%
  group_by(type, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Type of Larceny" = type) -> mc_larcenies_cat

mc_larcenies %>%
  group_by(value, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Monetary Value" = value) -> mc_larcenies_val

```

```{r WUMC Flextables Knit, echo = FALSE}
flextable(mc_crimeCat) %>%
  autofit() -> flex01

flextable(mc_dayNight) %>%
  autofit() -> flex02

flextable(mc_larcenies_cat) %>%
  autofit() -> flex03

flextable(mc_larcenies_val) %>%
  autofit() -> flex04

# add to powerpoint
report%>%
  add_slide()%>%
  ph_with("Washington University Medical Campus: Summary Tables", 
               location = ph_location_type(
                 type = "title"))%>%
  phl_with_flextable(olay = offlayout, 2, flex01)%>%
  phl_with_flextable(olay = offlayout, 3, flex02)%>%
  phl_with_flextable(olay = offlayout, 4, flex03)%>%
  phl_with_flextable(olay = offlayout, 5, flex04) -> report
```

## Washington University Medical Center: Total Crime Map

```{r MC color palette, include = FALSE}
sub <- filter(mc_crimes_month20_sf, neighborhood == 38)
col <- character(0)
if("Aggravated Assault" %in% sub$crimeCatName){col <- c("Aggravated Assault" = "#e41a1c")}
if("Arson" %in% sub$crimeCatName){col <- c(col, "Arson" = "#A65628")}
if("Burgalry" %in% sub$crimeCatName){col <- c(col, "Burgalry" = "#377eb8")}
if("Homicide" %in% sub$crimeCatName){col <- c(col, "Homicide" = "#FFFF33")}
if("Larceny" %in% sub$crimeCatName){col <- c(col, "Larceny" = "#4DAF4A")}
if("Motor Vehicle Theft" %in% sub$crimeCatName){col <- c(col, "Motor Vehicle Theft" = "#984EA3")}
if("Robbery" %in% sub$crimeCatName){col <- c(col, "Robbery" = "#FF7F00")}
```

```{r MC Total Crime Prep, include = FALSE}
cwe_mc_tm <- tm_shape(mc_tiles) +
  tm_rgb() +
  nhoods_sf %>%
  filter(., neighborhood == 38) %>%
  tm_shape() +
    tm_borders(col = "black",
               lwd = 2,
               lty = "dashed") +
  tm_shape(med_campus) +
    tm_fill(col = "#9ecae1",
            alpha = .5) +
    tm_borders(col = "black",
               lwd = 1,
               lty = "solid") +
  tm_shape(mc_crimes_month20_sf) +
    tm_bubbles(size = .25,
               col = "crimeCatName",
               palette = col,
               title.col = "Part 1 Crimes") +
  tm_credits("© Mapbox, © OpenStreetMap", position = c("left", "BOTTOM")) +
  tm_layout(
    frame = FALSE,
    legend.bg.color = "white",
    legend.frame=TRUE,
    legend.outside = TRUE,
    legend.position = c("right", "bottom"))

tmap_save(cwe_mc_tm, file = here("results", params$year, params$month, "cwe", "mc_total_crimes.jpeg"), width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "cwe", "mc_total_crimes.jpeg"), width = 9, height = 5), location = ph_location_type(type="body"), use_loc_size = FALSE)%>%
  ph_with("Washington University Medical Center: Total Crime Map", 
               location = ph_location_type(
                 type = "title") )-> report
```

## Cortex: Total Crime Map

```{r Cortex color palette, include = FALSE}
sub <- filter(ctx_crimes_sf, neighborhood == 38)
col <- character(0)
if("Aggravated Assault" %in% sub$crimeCatName){col <- c("Aggravated Assault" = "#e41a1c")}
if("Arson" %in% sub$crimeCatName){col <- c(col, "Arson" = "#A65628")}
if("Burgalry" %in% sub$crimeCatName){col <- c(col, "Burgalry" = "#377eb8")}
if("Homicide" %in% sub$crimeCatName){col <- c(col, "Homicide" = "#FFFF33")}
if("Larceny" %in% sub$crimeCatName){col <- c(col, "Larceny" = "#4DAF4A")}
if("Motor Vehicle Theft" %in% sub$crimeCatName){col <- c(col, "Motor Vehicle Theft" = "#984EA3")}
if("Robbery" %in% sub$crimeCatName){col <- c(col, "Robbery" = "#FF7F00")}
```

```{r Cortex Total Crime Prep, include = FALSE}
cwe_ctx_tm <- tm_shape(ctx_tiles) +
  tm_rgb() +
  nhoods_sf %>%
  filter(., neighborhood == 38) %>%
  tm_shape() +
    tm_borders(col = "black",
               lwd = 2,
               lty = "dashed") +
  tm_shape(cortex) +
    tm_fill(col = "#9ecae1",
            alpha = .5) +
    tm_borders(col = "black",
               lwd = 1,
               lty = "solid") +
  tm_shape(ctx_crimes_sf) +
    tm_bubbles(size = .25,
               col = "crimeCatName",
               palette = col,
               title.col = "Part 1 Crimes") +
  tm_credits("© Mapbox, © OpenStreetMap", position = c("left", "BOTTOM")) +
  tm_layout(
    frame = FALSE,
    legend.bg.color = "white",
    legend.frame=TRUE,
    legend.outside = TRUE,
    legend.position = c("right", "bottom"))

tmap_save(cwe_ctx_tm, file = here("results", params$year, params$month, "cwe", "ctx_total_crimes.jpeg"), width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "cwe", "ctx_total_crimes.jpeg"), width = 9, height = 5), location = ph_location_type(type="body"), use_loc_size = FALSE)%>%
  ph_with("Cortex: Total Crime Map", 
               location = ph_location_type(
                 type = "title") )-> report
```

## District 5: Crime Rates Map

```{r District 5 Density Map Prep, include = FALSE}
dst5_rateMap <- tm_shape(dst5_tiles) +
  tm_rgb() +
  tm_shape(dst_5_pop_sf) +
  tm_polygons(col = "crimeRate",
              palette = "BuPu",
              style = "jenks",
              title = "Crimes per 1,000 Residents") +
  tm_text("neighborhood", shadow=TRUE) +
  tm_layout(
    frame = FALSE,
    legend.bg.color = "white",
    legend.frame=TRUE,
    legend.outside = TRUE,
    legend.position = c("right", "bottom"))

tmap_save(dst5_rateMap, file = here("results", params$year, params$month, "district-5", "dst5_rates.jpeg"), width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "district-5", "dst5_rates.jpeg"), width = 9, height = 5), location = ph_location_type(type="body"), use_loc_size = FALSE)%>%
  ph_with("District 5: Crime Rates Map", 
               location = ph_location_type(
                 type = "title") )-> report
```

## District 5: Density Map Explanation

```{r District 5 Density Map Explanation Prep, include = FALSE}
library(qwraps2)
options(qwraps2_markup = "markdown")

dst_5_pop_sf <- as.data.frame(dst_5_pop_sf)
summary_statistics <-
  list(
    "Crime Rates" =
      list(
        "mean" = ~mean(crimeRate, na_rm = TRUE),
        "min" = ~min(crimeRate, na.rm = TRUE),
        "max" = ~max(crimeRate, na.rm = TRUE)),
    "Crime Total" =
      list(
        "mean" = ~mean(crimeTotal, na_rm = TRUE),
        "min" = ~min(crimeTotal, na.rm = TRUE),
        "max" = ~max(crimeTotal, na.rm = TRUE)))

dst_5_table <- summary_table(dst_5_pop_sf, summary_statistics)

print(dst_5_table,
      cnames = "Summary Statistics")

dst_5_rate_mean <- mean(dst_5_pop_sf$crimeRate)
dst_5_rate_mean

dst_5_min <- dst_5_pop_sf[which.min(dst_5_pop_sf$crimeRate),]
dst_5_min_rate_nhd <- print(dst_5_min$NHD_NAME, max.levels = 0)
dst_5_min_rate <- print(dst_5_min$crimeRate, max.levels = 0)

dst_5_max <- dst_5_pop_sf[which.max(dst_5_pop_sf$crimeRate),]
dst_5_max_rate_nhd <- print(dst_5_max$NHD_NAME, max.levels = 0)
dst_5_max_rate <- print(dst_5_max$crimeRate, max.levels = 0)

dst_5_total_mean <- mean(dst_5_pop_sf$crimeTotal)
dst_5_total_mean

dst_5_minT <- dst_5_pop_sf[which.min(dst_5_pop_sf$crimeTotal),]
dst_5_min_tot_nhd <- print(dst_5_minT$NHD_NAME, max.levels = 0)
dst_5_min_tot <- print(dst_5_minT$crimeTotal, max.levels = 0)

dst_5_maxT <- dst_5_pop_sf[which.max(dst_5_pop_sf$crimeTotal),]
dst_5_max_tot_nhd <- print(dst_5_maxT$NHD_NAME, max.levels = 0)
dst_5_max_tot <- print(dst_5_maxT$crimeTotal, max.levels = 0)

# add to powerpoint
report%>%
    add_slide(layout = 'Title and Content', master = 'Office Theme')%>%
  ph_with(value = "District 5: Density Map Explanation", location = ph_location_type(type = "title"))%>%
    ph_with(block_list(fpar(ftext("There are 15 neighborhoods in District 5", fp_text(color = "black", font.size = 24)))), location = ph_location_type(type = "body"))%>%
    ph_add_par()%>%
    ph_add_text(str = paste(" in one neighborhood was ", dst_5_min_tot, " (", dst_5_min_tot_nhd, ")", sep = ""), style = fp_text(color = "black", font.size = 24)) %>%
    ph_add_text(str = "The minimum number of crimes ", 
                style = fp_text(color = "#00B050", font.size = 24))%>%
    ph_add_par()%>%
    ph_add_text(str = paste("in one neighborhood was ", dst_5_max_tot, " (", dst_5_max_tot_nhd, ")", sep = ""), style = fp_text(color = "black", font.size = 24))%>%
    ph_add_text(str = "The maximum number of crimes ",
                style = fp_text(color = "red", font.size = 24))%>%
    ph_add_par()%>%
    ph_add_text(str = paste("in one neighborhood was", round(dst_5_total_mean, digits = 2), 
                            sep = " "), style = fp_text(color = "black", font.size = 24))%>%
    ph_add_text(str = "The mean number of crimes ",
                style = fp_text(color = "#00B0F0", font.size = 24))%>%
    ph_add_par()%>%
    ph_add_text(str = paste("in one neighborhood was ", round(dst_5_min_rate, digits = 2), " (", dst_5_min_rate_nhd, ")", sep = ""),
                style = fp_text(color = "black", font.size = 24))%>%
    ph_add_text(str = "The minimum rate of crimes ",
                style = fp_text(color = "#00B050", font.size = 24))%>%
    ph_add_par()%>%
    ph_add_text(str = paste("in one neighborhood was ", round(dst_5_max_rate, digits = 2), " (", dst_5_max_rate_nhd, ")", sep = ""),
                style = fp_text(color = "black", font.size = 24))%>%
    ph_add_text(str = "The maximum rate of crimes ",
                style = fp_text(color = "red", font.size = 24))%>%
    ph_add_par()%>%
    ph_add_text(str = paste("in one neighborhood was", round(dst_5_rate_mean, digits = 2), 
                            sep = " "), style = fp_text(color = "black", font.size = 24))%>%
    ph_add_text(str = "The mean rate of crimes ",
                style = fp_text(color = "#00B0F0", font.size = 24)) -> report
```

## Forest Park Southeast: Neighborhood Detail
### Appendix 1

```{r}
report%>%
  add_slide(layout = "Title Slide", master = "Office Theme")%>%
  ph_with(value = "Forest Park Southeast: Neighborhood Detail", location = ph_location_type(type = "ctrTitle"))%>%
  ph_with("Appendix 1", location = ph_location_type(type = "subTitle")) -> report
```

## Forest Park Southeast: Time of Crimes Map

```{r FPSE Day & Night Prep, include = FALSE}
fpse_dn_tm <- tm_shape(fpse_tiles) +
  tm_rgb() +
  nhoods_sf %>%
  filter(., neighborhood == 39) %>%
  tm_shape() +
    tm_fill(col = "#9ecae1",
            alpha = .5) +
    tm_borders(col = "black",
               lwd = 2,
               lty = "dashed") +
  filter(monthCrimes20_sf,
         neighborhood == 39) %>%
  tm_shape() +
    tm_bubbles(size = .25,
               col = "dayNight",
               palette = "-RdBu",
               title.col = "Time of Crimes") +
  tm_credits("© Mapbox, © OpenStreetMap", position = c("left", "BOTTOM")) +
  tm_layout(
    frame = FALSE,
    legend.bg.color = "white",
    legend.frame=TRUE,
    legend.outside = TRUE,
    legend.position = c("right", "bottom"))

tmap_save(fpse_dn_tm, file = here("results", params$year, params$month, "fpse", "fpse_day_night.jpeg"), width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "fpse", "fpse_day_night.jpeg"), width = 9, height = 5), location = ph_location_type(type = "body"), use_loc_size = FALSE)%>%
  ph_with("Forest Park Southeast: Time of Crimes Map", 
               location = ph_location_type(
                 type = "title") )-> report
```

## Forest Park Southeast: Violent Crime Map

```{r FPSE Violent Crime Map Prep, include = FALSE}
fpse_vlnt_tm <- tm_shape(fpse_tiles) +
  tm_rgb() +
  nhoods_sf %>%
  filter(., neighborhood == 39) %>%
  tm_shape() +
    tm_fill(col = "#9ecae1",
            alpha = .5) +
    tm_borders(col = "black",
               lwd = 2,
               lty = "dashed") +
  filter(monthCrimes20_sf,
         neighborhood == 39) %>%
  tm_shape() +
    tm_bubbles(size = .25,
               col = "violent",
               palette = "Reds",
               title.col = "Violent") +
  tm_credits("© Mapbox, © OpenStreetMap", position = c("left", "BOTTOM")) +
  tm_layout(
    frame = FALSE,
    legend.bg.color = "white",
    legend.frame=TRUE,
    legend.outside = TRUE,
    legend.position = c("right", "bottom"))

tmap_save(fpse_vlnt_tm, file = here("results", params$year, params$month, "fpse", "fpse_vlnt.jpeg"), width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "fpse", "fpse_vlnt.jpeg"), width = 9, height = 5), location = ph_location_type(type = "body"), use_loc_size = FALSE)%>%
  ph_with("Forest Park Southeast: Violent Crime Map", 
               location = ph_location_type(
                 type = "title") )-> report
```

## Forest Park Southeast: Crime Density Map

```{r FPSE Density Map Prep, include = FALSE}
monthCrimes20_sf %>%
  filter(neighborhood == 39) %>%
  smooth_map(., bandwidth = 0.5, style = "pretty",
  cover = fpse) -> fpse_densities

fpse_den_tm <- tm_shape(fpse_tiles) +
  tm_rgb() +
  nhoods_sf %>%
  filter(., neighborhood == 39) %>%
  tm_shape() +
    tm_fill(col = NA,
            alpha = .5) +
    tm_borders(col = "black",
               lwd = 2,
               lty = "dashed") +
  tm_shape(fpse_densities$polygons) +
  tm_fill(col = "level", palette = "BuPu", alpha = .60,
    title = expression("Crimes per " * km^2)) +
  tm_credits("© Mapbox, © OpenStreetMap", position = c("left", "BOTTOM")) +
  tm_layout(
    frame = FALSE,
    legend.bg.color = "white",
    legend.frame=TRUE,
    legend.outside = TRUE,
    legend.position = c("right", "bottom"))

tmap_save(fpse_den_tm, file = here("results", params$year, params$month, "fpse", "fpse_density.jpeg"), width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "fpse", "fpse_density.jpeg"), width = 9, height = 5), location = ph_location_type(type = "body"), use_loc_size = FALSE)%>%
  ph_with("Forest Park Southeast: Crime Density Map", 
               location = ph_location_type(
                 type = "title") )-> report
```

## Grove Community Improvement District: Total Crime Map

```{r Grove CID color palette, include = FALSE}
grove_crimes <- st_intersection(monthCrimes20_sf, grove_cid)
sub <- filter(grove_crimes, neighborhood == 39)
col <- character(0)
if("Aggravated Assault" %in% sub$crimeCatName){col <- c("Aggravated Assault" = "#e41a1c")}
if("Arson" %in% sub$crimeCatName){col <- c(col, "Arson" = "#A65628")}
if("Burgalry" %in% sub$crimeCatName){col <- c(col, "Burgalry" = "#377eb8")}
if("Homicide" %in% sub$crimeCatName){col <- c(col, "Homicide" = "#FFFF33")}
if("Larceny" %in% sub$crimeCatName){col <- c(col, "Larceny" = "#4DAF4A")}
if("Motor Vehicle Theft" %in% sub$crimeCatName){col <- c(col, "Motor Vehicle Theft" = "#984EA3")}
if("Robbery" %in% sub$crimeCatName){col <- c(col, "Robbery" = "#FF7F00")}
```

```{r Grove CID Total Crime Prep, include = FALSE}
fpse_grove_tm <- tm_shape(grv_tiles) +
  tm_rgb() +
  nhoods_sf %>%
  filter(., neighborhood == 39) %>%
  tm_shape() +
    tm_borders(col = "black",
               lwd = 2,
               lty = "dashed") +
  tm_shape(grove_cid) +
    tm_fill(col = "#9ecae1",
            alpha = .5) +
    tm_borders(col = "black",
               lwd = 1,
               lty = "solid") +
  tm_shape(grove_crimes) +
    tm_bubbles(size = .25,
               col = "crimeCatName",
               palette = col,
               title.col = "Part 1 Crimes") +
  tm_credits("© Mapbox, © OpenStreetMap", position = c("left", "BOTTOM")) +
  tm_layout(
    frame = FALSE,
    legend.bg.color = "white",
    legend.frame=TRUE,
    legend.outside = TRUE,
    legend.position = c("right", "bottom"))

tmap_save(fpse_grove_tm, file = here("results", params$year, params$month, "fpse", "fpse_grove.jpeg"), width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "fpse", "fpse_grove.jpeg"), width = 9, height = 5), location = ph_location_type(type = "body"), use_loc_size = FALSE)%>%
  ph_with("Grove Community Improvement District: Total Crime Map", 
               location = ph_location_type(
                 type = "title") )-> report
```

## Forest Park Southeast: Larceny Breakdown

```{r FPSE Larceny Breakdown Prep, include = FALSE}
larceny %>%
  filter(., neighborhood == 39) %>%
  group_by(weekday, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Day of the Week" = weekday) -> fpse_larcenies_weekDay

larceny %>%
  filter(., neighborhood == 39) %>%
  group_by(dayNight, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Time of Day" = dayNight) -> fpse_larcenies_dayNight

larceny %>%
  filter(., neighborhood == 39) %>%
  group_by(type, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Type of Larceny" = type) -> fpse_larcenies_type

larceny %>%
  filter(., neighborhood == 39) %>%
  group_by(value, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Monetary" = value) -> fpse_larcenies_value
```

```{r FPSE Larceny Tables Knit, echo = FALSE}
flextable(fpse_larcenies_weekDay) %>%
  autofit() -> flex01

flextable(fpse_larcenies_dayNight) %>%
  autofit() -> flex02

flextable(fpse_larcenies_type) %>%
  autofit() -> flex03

flextable(fpse_larcenies_value) %>%
  autofit() -> flex04

# add to powerpoint
report%>%
  add_slide()%>%
  ph_with("Forest Park Southeast: Larceny Breakdown", 
               location = ph_location_type(
                 type = "title"))%>%
  phl_with_flextable(olay = offlayout, 2, flex01)%>%
  phl_with_flextable(olay = offlayout, 3, flex02)%>%
  phl_with_flextable(olay = offlayout, 4, flex03)%>%
  phl_with_flextable(olay = offlayout, 5, flex04) -> report
```

## Forest Park Southeast: Total Crimes by Days of the Week

```{r FPSE Crime by Weekday Graph Prep, include= FALSE}
monthCrimes20 %>%
  filter(., neighborhood == 39) %>%
  group_by(weekday, .drop = FALSE) %>%
  count() %>%
  replace(., is.na(.), 0) -> fpse_weekDay

wkdys[!(wkdys %in% fpse_weekDay$weekday)] -> missing_category_days
is_empty(missing_category_days) -> test

as.data.frame(fpse_weekDay) -> fpse_weekDay

if(test == FALSE) {
   add_row(fpse_weekDay, weekday = missing_category_days) -> fpse_weekDay
}

  ggplot(fpse_weekDay, aes(x=weekday, y=n, group = 1)) +
    geom_line(color="blue") +
    geom_point() +
    xlab("Day of Week") + ylab("Total Crimes")

ggsave(here("results", params$year, params$month, "fpse", "fpse_crime_weekday_graph.jpeg"), dpi = 500)

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "fpse", "fpse_crime_weekday_graph.jpeg"), width = 9, height = 5.45),
          location = ph_location_type(type = "body"), use_loc_size = FALSE)%>%
  ph_with("Forest Park Southeast: Total Crimes by Days of the Week", 
               location = ph_location_type(
                 type = "title") )-> report
```

## Forest Park Southeast: Crimes by Time of Day

```{r FPSE Crime by Time of Day Graph Prep, include = FALSE }
monthCrimes20 %>%
  filter(., neighborhood == 39) %>%
  group_by(dayNight, .drop = FALSE) %>%
  count() %>%
  ggplot(., aes(x=dayNight, y=n, fill = dayNight)) +
    geom_bar(stat="identity", position=position_dodge(), colour="black") +
    xlab("Time of Day") + ylab("Total Crimes") +
    labs(fill = "Time")

ggsave(here("results", params$year, params$month, "fpse", "fpse_crime_timeDay_graph.jpeg"), width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "fpse", "fpse_crime_timeDay_graph.jpeg"), width = 9, height = 5),
          location = ph_location_type(type = "body"), use_loc_size = FALSE)%>%
  ph_with("Forest Park Southeast: Crimes by Time of Day", 
               location = ph_location_type(
                 type = "title") )-> report
```

## Forest Park Southeast: Crimes by Day & Category

```{r FPSE Crime by Category Weekday Graph Prep, include= FALSE}
monthCrimes20 %>%
  filter(., neighborhood == 39) %>%
  group_by(crimeCatName, .drop = FALSE) %>%
  ggplot(., aes(weekday)) +
    geom_bar(aes(fill = crimeCatName), position=position_dodge(), colour="black") +
    scale_colour_manual(
    values = cols,
    aesthetics = c("colour", "fill")
    ) +
    xlab("Day of Week") + ylab("Total Crimes") +
    labs(fill = "Part 1 Crimes")

ggsave(here("results", params$year, params$month, "fpse", "fpse_crimeCat_weekday_graph.jpeg"),
       width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "fpse", "fpse_crimeCat_weekday_graph.jpeg"), width = 9, height = 5),
          location = ph_location_type(type = "body"), use_loc_size = FALSE)%>%
  ph_with("Forest Park Southeast: Crimes by Day & Category", 
               location = ph_location_type(
                 type = "title") )-> report
```

## Central West End: Neighborhood Detail
### Appendix 2

```{r}
report%>%
  add_slide(layout = "Title Slide", master = "Office Theme")%>%
  ph_with(value = "Central West End: Neighborhood Detail", location = ph_location_type(type = "ctrTitle"))%>%
  ph_with("Appendix 2", location = ph_location_type(type = "subTitle")) -> report
```

## Central West End: Time of Crimes Map

```{r CWE Time of Crimes Map Prep, include = FALSE}
cwe_dn_tm <- tm_shape(cwe_tiles) +
  tm_rgb() +
  nhoods_sf %>%
  filter(., neighborhood == 38) %>%
  tm_shape() +
    tm_fill(col = "#9ecae1",
            alpha = .5) +
    tm_borders(col = "black",
               lwd = 2,
               lty = "dashed") +
  filter(monthCrimes20_sf,
         neighborhood == 38) %>%
  tm_shape() +
    tm_bubbles(size = .25,
               col = "dayNight",
               palette = "-RdBu",
               title.col = "Time of Crimes") +
  tm_credits("© Mapbox, © OpenStreetMap", position = c("left", "BOTTOM")) +
  tm_layout(
    frame = FALSE,
    legend.bg.color = "white",
    legend.frame=TRUE,
    legend.outside = TRUE,
    legend.position = c("right", "bottom"))

tmap_save(cwe_dn_tm, file = here("results", params$year, params$month, "cwe", "cwe_day_night.jpeg"), width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "cwe", "cwe_day_night.jpeg"), width = 9, height = 5), location = ph_location_type(type="body"), use_loc_size = FALSE)%>%
  ph_with("Central West End: Time of Crime Map", 
               location = ph_location_type(
                 type = "title") )-> report
```

## Central West End: Violent Crime Map

```{r CWE Violent Crime Map Prep, include = FALSE}
cwe_vlnt_tm <- tm_shape(cwe_tiles) +
  tm_rgb() +
  nhoods_sf %>%
  filter(., neighborhood == 38) %>%
  tm_shape() +
    tm_fill(col = "#9ecae1",
            alpha = .5) +
    tm_borders(col = "black",
               lwd = 2,
               lty = "dashed") +
  filter(monthCrimes20_sf,
         neighborhood == 38) %>%
  tm_shape() +
    tm_bubbles(size = .25,
               col = "violent",
               palette = "Reds",
               title.col = "Violent") +
  tm_credits("© Mapbox, © OpenStreetMap", position = c("left", "BOTTOM")) +
  tm_layout(
    frame = FALSE,
    legend.bg.color = "white",
    legend.frame=TRUE,
    legend.outside = TRUE,
    legend.position = c("right", "bottom"))

tmap_save(cwe_vlnt_tm, file = here("results", params$year, params$month, "cwe", "cwe_vlnt.jpeg"), width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "cwe", "cwe_vlnt.jpeg"), width = 9, height = 5), location = ph_location_type(type="body"), use_loc_size = FALSE)%>%
  ph_with("Central West End: Violent Crime Map", 
               location = ph_location_type(
                 type = "title") )-> report
```

## Central West End: Crime Density Map

```{r CWE Density Map Prep, include = FALSE}
monthCrimes20_sf %>%
  filter(neighborhood == 38) %>%
  smooth_map(., bandwidth = 0.5, style = "pretty",
  cover = cwe) -> cwe_densities

cwe_den_tm <- tm_shape(cwe_tiles) +
  tm_rgb() +
  nhoods_sf %>%
  filter(., neighborhood == 38) %>%
  tm_shape() +
    tm_fill(col = NA,
            alpha = .5) +
    tm_borders(col = "black",
               lwd = 2,
               lty = "dashed") +
  tm_shape(cwe_densities$polygons) +
  tm_fill(col = "level", palette = "BuPu", alpha = .60,
    title = expression("Crimes per " * km^2)) +
  tm_credits("© Mapbox, © OpenStreetMap", position = c("left", "BOTTOM")) +
  tm_layout(
    frame = FALSE,
    legend.bg.color = "white",
    legend.frame=TRUE,
    legend.outside = TRUE,
    legend.position = c("right", "bottom"))

tmap_save(cwe_den_tm, file = here("results", params$year, params$month, "cwe", "cwe_density.jpeg"), width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "cwe", "cwe_density.jpeg"), width = 9, height = 5), location = ph_location_type(type="body"), use_loc_size = FALSE)%>%
  ph_with("Central West End: Crime Density Map", 
               location = ph_location_type(
                 type = "title") )-> report
```

## Central West End: Larceny Breakdown

```{r CWE Larceny Breakdown Prep, include = FALSE}
larceny %>%
  filter(., neighborhood == 38) %>%
  group_by(weekday, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Day of the Week" = weekday) -> cwe_larcenies_weekDay

larceny %>%
  filter(., neighborhood == 38) %>%
  group_by(dayNight, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Time of Day" = dayNight) -> cwe_larcenies_dayNight

larceny %>%
  filter(., neighborhood == 38) %>%
  group_by(type, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Type of Larceny" = type) -> cwe_larcenies_type

larceny %>%
  filter(., neighborhood == 38) %>%
  group_by(value, .drop = FALSE) %>%
  count() %>%
  adorn_totals(., "row", name = "Total") %>%
  rename(., "Number of Crimes" = n, "Monetary Value" = value) -> cwe_larcenies_value

```

```{r CWE Larceny Breakdown Knit, echo = FALSE}
flextable(cwe_larcenies_weekDay) %>%
  autofit() -> flex01

flextable(cwe_larcenies_dayNight) %>%
  autofit() -> flex02

flextable(cwe_larcenies_type) %>%
  autofit() -> flex03

flextable(cwe_larcenies_value) %>%
  autofit() -> flex04

# add to powerpoint
report%>%
  add_slide()%>%
  ph_with("Central West End: Larceny Breakdown", 
               location = ph_location_type(
                 type = "title"))%>%
  phl_with_flextable(olay = offlayout, 2, flex01)%>%
  phl_with_flextable(olay = offlayout, 3, flex02)%>%
  phl_with_flextable(olay = offlayout, 4, flex03)%>%
  phl_with_flextable(olay = offlayout, 5, flex04) -> report
```

## Central West End: Total Crimes by Days of the Week

```{r CWE Crime by Weekday Graph Prep, include = FALSE}
monthCrimes20 %>%
  filter(., neighborhood == 38) %>%
  group_by(weekday, .drop = FALSE) %>%
  count() %>%
  replace(., is.na(.), 0) -> cwe_weekDay

wkdys[!(wkdys %in% cwe_weekDay$weekday)] -> missing_category_days
is_empty(missing_category_days) -> test

as.data.frame(cwe_weekDay) ->cwe_weekDay

if(test == FALSE) {
   add_row(cwe_weekDay, weekday = missing_category_days) -> cwe_weekDay
}

  ggplot(cwe_weekDay, aes(x=weekday, y=n, group = 1)) +
    geom_line(color="blue") +
    geom_point() +
    xlab("Day of Week") + ylab("Total Crimes")

ggsave(here("results", params$year, params$month, "cwe", "cwe_crime_weekday_graph.jpeg"), dpi = 500)

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "cwe", "cwe_crime_weekday_graph.jpeg"), width = 9, height = 5.45),
          location = ph_location_type(type = "body"), use_loc_size = FALSE)%>%
  ph_with("Central West End: Total Crimes by Days of the Week", 
               location = ph_location_type(
                 type = "title") )-> report
```

## Central West End: Crimes by Time of Day

```{r CWE Crime by Time of Day Graph Prep, include = FALSE }
monthCrimes20 %>%
  filter(., neighborhood == 38) %>%
  group_by(dayNight, .drop = FALSE) %>%
  count() %>%
  ggplot(., aes(x=dayNight, y=n, fill = dayNight)) +
    geom_bar(stat="identity", position=position_dodge(), colour="black") +
    xlab("Time of Day") + ylab("Total Crimes") +
    labs(fill = "Time")

ggsave(here("results", params$year, params$month, "cwe", "cwe_crime_timeDay_graph.jpeg"), width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "cwe", "cwe_crime_timeDay_graph.jpeg"), width = 9, height = 5),
          location = ph_location_type(type = "body"), use_loc_size = FALSE)%>%
  ph_with("Central West End: Crimes by Time of Day", 
               location = ph_location_type(
                 type = "title") )-> report
```

## Central West End: Crimes by Day & Category

```{r CWE Crime by Category Weekday Graph Prep, include= FALSE}
monthCrimes20 %>%
  filter(., neighborhood == 38) %>%
  group_by(crimeCatName, .drop = FALSE) %>%
  ggplot(., aes(weekday)) +
    scale_colour_manual(
    values = cols,
    aesthetics = c("colour", "fill")
    ) +
    geom_bar(aes(fill = crimeCatName), position=position_dodge(), colour="black") +
    xlab("Day of Week") + ylab("Total Crimes") +
    labs(fill = "Part 1 Crimes")

ggsave(here("results", params$year, params$month, "cwe", "cwe_crimeCat_weekday_graph.jpeg"), width = 9, height = 5, units = "in")

#add to powerpoint report
report%>%
  add_slide()%>%
  ph_with(external_img(here::here("results", params$year, params$month, "cwe", "cwe_crimeCat_weekday_graph.jpeg"), width = 9, height = 5),
          location = ph_location_type(type = "body"), use_loc_size = FALSE)%>%
  ph_with("Central West End: Crimes by Day & Category", 
               location = ph_location_type(
                 type = "title") )-> report
```

```{r}
# save powerpoint report
print(report, target = here::here("results", "presentations",  params$year, params$month, paste("fpse-bot-cwe-mc-", params$month, params$year, ".pptx", sep = "")))
```

```{r}
# This code cleans our Global Environment.

rm(list = ls())

print("Great job! The code ran all the way through. You did AMAZING!")
```