---
title: "PDF Data Extraction"
output: html_document
params:
  #Month1/month2 are the first 3 letters of the  month in a given 2 month period (see https://www.slmpd.org/crime_stats.shtml)
  month: "Jan"
  year: "2022"
  year2: "2021"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#IMPORTANT
This notebook needs to be manually updated both in the paramaters and, possibly, on lines 71 and 87. Refer to the `How-To-Instructions.Rmd` for more information.

#Load Dependencies
```{r}
library(pdftools)   #pdf data extraction
library(dplyr)      #tools for cleaning data
library(here)       #file path management
library(stringr)      #string manipulation
library(grid)         #inset map
library(gateway)      #load stl spatial data
library(tmap)         #tools for mapping

#Load Data
df <- pdf_text(here::here("NIBRS", "data", params$year, params$month, paste(params$month, "-crime.pdf", sep = "")))
```

# Neighborhood Index
```{r}
#Format: c(first page, second page, neighborhood number)
bot <- c(11,12,28)
cwe <- c(23,24,38)
fpse <- c(55,56,39)
sdbp <- c(131, 132,46)
dbp <- c(39,40,47)
we <- c(173,174,48)
vp <- c(165,166,49)
ac <- c(1,2,51)
fp <- c(57,58,53)
lp <- c(87,88,54)
vd <- c(163,164,58)
```

#Create scrape_pdf Function
`table` refers to the PDF that you want to extract from
`neighborhood` should be set to the neighborhood object you want evaluated (created in the neighborhood index section above).
`month` is the current month
`year` is the current year
`year2` is the previous year`
```{r}
scrape_pdf <- function(table, neighborhood, year, year2) {
  #create table of neighborhood data based on PDF page number
  data <- table[neighborhood[1]]
  #split elements of string based on line breaks
  data <- strsplit(data, "\n")
  data <- data[[1]]
  #remove leading and trailing whitespaces
  data <- trimws(data)
  #gather first page of data using text at the beginning and end of the page
  data <- data[grep("Murder and Nonnegligent Manslaughter", data):grep("Wire Fraud", data)]
  data <- str_split_fixed(data, " {2,}", 7)
  #convert to dataframe
  data <- data.frame(data, stringsAsFactors = FALSE)
  #remove empty data/titles
  data <- data[-c(18:22),]
  #rename columns
  names(data) <- c("Crime", "NIBRS",
                           year,
                           year2, 
                           "Diff",
                           "Change",
                           "YTD")
  #repeat for page 2 of data
  data2 <- table[neighborhood[2]]
  data2 <- strsplit(data2, "\n")
  data2 <- data2[[1]]
  data2 <- trimws(data2)
  data2 <- data2[grep("Embezzlement", data2):grep("All Other Offenses", data2)]
  data2 <- str_split_fixed(data2, " {2,}", 7)
  data2 <- data.frame(data2, stringsAsFactors = FALSE)
  data2 <- data2[-c(6:10, 31:37),]
  names(data2) <- c("Crime", "NIBRS",
                           year,
                           year2,
                           "Diff",
                           "Change",
                           "YTD")
  data <- bind_rows(data, data2)
  data <- data%>%
    #assign neighborhood number
    mutate(nbhd_num = neighborhood[3])%>%
    #assign category based on row number
    mutate(type = ifelse(row_number() %in% 1:16, "Person",
                                     ifelse(row_number() %in% 17:42, "Property",
                                     ifelse(row_number() %in% 43:62, "Society",
                                     ifelse(row_number() %in% 63:64, "Unspecified", NA)))))
  cols.num <- c(params$year, params$year2)
  data[cols.num] <- sapply(data[cols.num],as.numeric) #convert crime columns to numeric
  
  #remove unnecessary columns
  data <- data[-c(2, 5:7)]
  
  return(data)
}
```

```{r}
#scrape pdf for each neighborhood
bot_df <- scrape_pdf(df, bot, params$year, params$year2)
cwe_df <- scrape_pdf(df, cwe, params$year, params$year2)
fpse_df <- scrape_pdf(df, fpse, params$year, params$year2)
sdbp_df <- scrape_pdf(df, sdbp, params$year, params$year2)
dbp_df <- scrape_pdf(df, dbp, params$year, params$year2)
we_df <- scrape_pdf(df, we, params$year, params$year2)
vp_df <- scrape_pdf(df, vp, params$year, params$year2)
ac_df <- scrape_pdf(df, ac, params$year, params$year2)
fp_df <- scrape_pdf(df, fp, params$year, params$year2)
lp_df <- scrape_pdf(df, lp, params$year, params$year2)
vd_df <- scrape_pdf(df, vd, params$year, params$year2)
#get totals for all neighborhoods
nbhd_bind <- bind_rows(bot_df, cwe_df, fpse_df, sdbp_df, dbp_df, we_df, vp_df, ac_df, fp_df, lp_df, vd_df)
#Add neighborhood names column
nbhd_bind <- mutate(nbhd_bind, nbhd_name = ifelse(grepl("28", nbhd_num), "Botanical Heights",
                            ifelse(grepl("38", nbhd_num), "Central West End",
                                             ifelse(grepl("39", nbhd_num), "Forest Park Southeast",
                                             ifelse(grepl("46", nbhd_num), "Skinker DeBaliviere",  
                                             ifelse(grepl("47", nbhd_num), "DeBaliviere Place",
                                             ifelse(grepl("48", nbhd_num), "West End",
                                             ifelse(grepl("49", nbhd_num), "Visitation Park",       
                                             ifelse(grepl("51", nbhd_num), "Academy",       
                                             ifelse(grepl("53", nbhd_num), "Fountain Park",       
                                             ifelse(grepl("54", nbhd_num), "Lewis Place",       
                                             ifelse(grepl("58", nbhd_num), "Vandeventer", NA))))))))))))

nbhd_bind$Crime[nbhd_bind$Crime == "Credit Card/Automatic Teller Machine Fraud"] <- "Credit Card/ATM Fraud"
nbhd_bind$Crime[nbhd_bind$Crime == "Theft From Motor Vehicle"] <- "Theft From MV"
nbhd_bind$Crime[nbhd_bind$Crime == "Theft From Motor Vehicle Parts/Accessories"] <- "Theft From MV Parts/Accessories"
nbhd_bind$Crime[nbhd_bind$Crime == "Motor Vehicle Theft"] <- "MV Theft"

select(nbhd_bind, -params$year) -> nbhd_bind_PY
select(nbhd_bind, -params$year2) -> nbhd_bind

names(nbhd_bind_PY) <- c("Crime",
                           params$month,
                           "nbhd_num",
                           "type",
                           "nbhd_name")

names(nbhd_bind) <- c("Crime",
                           params$month,
                           "nbhd_num",
                           "type",
                           "nbhd_name")

#Build master dataset to be added onto each month
if(params$month == "Jan"){
  basePY <- nbhd_bind_PY
  base <- nbhd_bind
  save(basePY, base, file = here::here("NIBRS", "data", params$year, "base_data", "base_data.rda"))
}else{
  load(file = here::here("NIBRS", "data", params$year, "base_data", "base_data.rda"))
  basePY <- inner_join(basePY, nbhd_bind_PY)
  base <- inner_join(base, nbhd_bind)
  save(basePY, base, file = here::here("NIBRS", "data", params$year, "base_data", "base_data.rda"))
}

#save output
save(base, basePY, file = here::here("NIBRS", "data", params$year, params$month, "clean-crime-data.rda"))
```

